---
title: "Energy Systems & Medical Devices"
author: "Gian Teufen"
format:
  dashboard:
    nav-buttons: []
---

```{r setup}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(ggplot2)
library(patchwork)
library(gt)
library(ggrepel)
library(scales)
library(broom)

# ── Paths ─────────────────────────────────────────────────────────────────────
proj_root         <- normalizePath(file.path(getwd(), "../.."))
energy_data_path  <- file.path(proj_root, "data/derived_data")
devices_data_path <- "/home/teufeng/med-dev-database/data/derived_data"

plots_path <- file.path(energy_data_path, "plots/energy_and_devices")
dir.create(plots_path, showWarnings = FALSE, recursive = TRUE)

# ── Load data ─────────────────────────────────────────────────────────────────
energy_raw  <- read_rds(file.path(energy_data_path, "Combined_Questionnaire_Systems.rds"))
devices_raw <- read_rds(file.path(devices_data_path, "df_ana.rds"))

energy_raw  <- energy_raw  |> mutate(facility_id = as.integer(facility_id))
devices_raw <- devices_raw |> mutate(facility_id = as.integer(facility_id))

# ── Facility-level energy summary ─────────────────────────────────────────────
energy_fac <- energy_raw |>
  group_by(facility_id, facility_name = facility_name_energy, district, region) |>
  summarise(
    n_systems        = n(),
    n_functional     = sum(functional_now == "Yes",        na.rm = TRUE),
    n_partial        = sum(functional_now == "Partially",  na.rm = TRUE),
    n_nonfunctional  = sum(functional_now == "No",         na.rm = TRUE),
    pct_functional   = n_functional / n_systems,
    has_solar        = any(str_detect(type, "Solar"),      na.rm = TRUE),
    has_grid         = any(type == "Grid",                 na.rm = TRUE),
    has_generator    = any(type == "Generator",            na.rm = TRUE),
    n_energy_sources = sum(c(has_solar, has_grid, has_generator)),
    avg_nights_no_light = first(na.omit(night_treatments_in_darkness_monthly)),
    n_funders_energy = n_distinct(funding[!is.na(funding)]),
    mean_install_year = {
      yrs <- suppressWarnings(as.numeric(installation_year))
      yrs <- yrs[!is.na(yrs) & yrs > 2000]
      if (length(yrs) > 0) mean(yrs) else NA_real_
    },
    .groups = "drop"
  )

# ── Facility-level device summary ─────────────────────────────────────────────
devices_fac <- devices_raw |>
  filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
  group_by(facility_id) |>
  summarise(
    n_devices_total    = n(),
    n_fully_functional = sum(functionality == "fully functional",  na.rm = TRUE),
    n_dysfunctional    = sum(functionality == "dysfunctional",     na.rm = TRUE),
    n_partial_dev      = sum(functionality == "partly functional", na.rm = TRUE),
    pct_dev_functional = n_fully_functional / n_devices_total,
    pct_dysfunctional  = n_dysfunctional    / n_devices_total,
    n_med_devices      = sum(supercategory == "Medical Devices"),
    pct_med_functional = sum(supercategory == "Medical Devices" &
                               functionality == "fully functional", na.rm = TRUE) /
                         pmax(sum(supercategory == "Medical Devices"), 1),
    # Share of devices that need electricity (AC or DC)
    n_powered          = sum(supercategory == "Medical Devices" &
                               power_type %in% c("AC", "DC", "both"), na.rm = TRUE),
    pct_powered        = n_powered / pmax(n_med_devices, 1),
    n_funders_devices  = n_distinct(funding_primary[
      !is.na(funding_primary) &
        !funding_primary %in% c("not applicable", "unknown")]),
    simpson_funder_dev = {
      f <- funding_primary[!is.na(funding_primary) &
                             !funding_primary %in% c("not applicable", "unknown")]
      if (length(f) == 0) NA_real_
      else { p <- table(f) / length(f); 1 - sum(p^2) }
    },
    mean_delivery_year = {
      yrs <- suppressWarnings(as.numeric(year_delivered))
      yrs <- yrs[!is.na(yrs) & yrs > 2000]
      if (length(yrs) > 0) mean(yrs) else NA_real_
    },
    .groups = "drop"
  )

# ── Combined ──────────────────────────────────────────────────────────────────
combined <- inner_join(energy_fac, devices_fac, by = "facility_id") |>
  arrange(facility_id)

# ── Funder overlap (Donor Governance analysis) ────────────────────────────────
norm_funder <- function(x) {
  x_lc <- str_trim(str_to_lower(as.character(x)))
  case_when(
    is.na(x) | x_lc == ""                                              ~ NA_character_,
    x_lc %in% c("moh", "staff", "egpaf", "gov", "government", "dho")  ~ "gov",
    x_lc %in% c("na", "n/a", "not applicable", "unknown")             ~ NA_character_,
    TRUE                                                                ~ x_lc
  )
}

energy_funder_sets <- energy_raw |>
  mutate(funder = norm_funder(funding)) |>
  filter(!is.na(funder)) |>
  group_by(facility_id) |>
  summarise(funders_e = list(sort(unique(funder))), .groups = "drop")

device_funder_sets <- devices_raw |>
  filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
  mutate(funder = norm_funder(funding_primary)) |>
  filter(!is.na(funder)) |>
  group_by(facility_id) |>
  summarise(funders_d = list(sort(unique(funder))), .groups = "drop")

funder_overlap_wide <- energy_funder_sets |>
  inner_join(device_funder_sets, by = "facility_id") |>
  mutate(
    n_shared     = map2_int(funders_e, funders_d, \(e, d) length(intersect(e, d))),
    n_union      = map2_int(funders_e, funders_d, \(e, d) length(union(e, d))),
    n_energy_only = map2_int(funders_e, funders_d, \(e, d) length(setdiff(e, d))),
    n_device_only = map2_int(funders_e, funders_d, \(e, d) length(setdiff(d, e))),
    jaccard      = if_else(n_union > 0, n_shared / n_union, NA_real_),
    is_co_funded = n_shared > 0
  )

energy_repair <- energy_raw |>
  filter(!is.na(repair_success)) |>
  group_by(facility_id) |>
  summarise(
    pct_repair_success = mean(repair_success == "Yes", na.rm = TRUE),
    n_repairs          = n(),
    .groups = "drop"
  )

energy_pm <- energy_raw |>
  group_by(facility_id) |>
  summarise(
    pm_raw = na.omit(preventive_maintenance_carried_out)[1],
    .groups = "drop"
  ) |>
  mutate(
    pm_score = case_when(
      pm_raw == "Routinely"                   ~ 1,
      pm_raw == "Sometimes but not routinely" ~ 0.5,
      pm_raw == "Never"                       ~ 0,
      TRUE                                     ~ NA_real_
    )
  ) |>
  select(facility_id, pm_score)

df_gov <- combined |>
  left_join(
    funder_overlap_wide |> select(facility_id, n_shared, jaccard, is_co_funded),
    by = "facility_id"
  ) |>
  left_join(energy_repair, by = "facility_id") |>
  left_join(energy_pm,     by = "facility_id") |>
  mutate(
    prop_energy_nonfunc = 1 - pct_functional,
    prop_device_nonfunc = pct_dysfunctional
  ) |>
  filter(!is.na(n_shared))

# Combined (energy + devices) funder Simpson diversity per facility
funder_pool <- bind_rows(
  energy_raw |>
    mutate(funder = norm_funder(funding)) |>
    filter(!is.na(funder)) |>
    select(facility_id, funder),
  devices_raw |>
    filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
    mutate(funder = norm_funder(funding_primary)) |>
    filter(!is.na(funder)) |>
    select(facility_id, funder)
)

simpson_combined_df <- funder_pool |>
  group_by(facility_id) |>
  summarise(
    simpson_combined = {
      f <- funder
      if (length(f) == 0) NA_real_
      else { p <- table(f) / length(f); as.numeric(1 - sum(p^2)) }
    },
    .groups = "drop"
  )

df_gov <- df_gov |>
  left_join(simpson_combined_df, by = "facility_id")

# ── Theme ─────────────────────────────────────────────────────────────────────
eth_blue  <- "#004D80"
eth_light <- "#0076BA"
# Okabe-Ito colorblind-safe palette
clr_yes   <- "#009E73"   # bluish-green
clr_no    <- "#D55E00"   # vermillion
clr_part  <- "#E69F00"   # orange

theme_eth <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title       = element_text(colour = eth_blue, face = "bold", size = 13),
      plot.subtitle    = element_text(colour = "grey40", size = 10),
      axis.title       = element_text(colour = "grey30", size = 10),
      panel.grid.minor = element_blank()
    )
}
```

# Overview

## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Facilities"
list(icon = "hospital", color = "primary", value = nrow(combined))
```

```{r}
#| content: valuebox
#| title: "Energy systems surveyed"
list(icon = "lightning-charge", color = "info", value = sum(energy_fac$n_systems))
```

```{r}
#| content: valuebox
#| title: "Medical & support devices"
list(icon = "cpu", color = "secondary", value = sum(devices_fac$n_devices_total))
```

```{r}
#| content: valuebox
#| title: "Facilities ≥1 functional energy system"
list(icon = "check-circle", color = "success", value = sum(combined$n_functional >= 1))
```

## Row {height="80%"}

```{r}
#| title: "Energy vs. device functionality"

p_overview <- combined |>
  ggplot(aes(x = pct_functional, y = pct_dev_functional)) +
  geom_smooth(method = "lm", se = TRUE, colour = eth_blue,
              fill = eth_light, alpha = 0.15, linewidth = 0.8) +
  geom_point(aes(size = n_devices_total, colour = pct_functional), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 3,
                  colour = "grey30", max.overlaps = 20) +
  scale_colour_viridis_c(labels = percent, name = "Energy\nfunctionality",
                         option = "D", direction = 1) +
  scale_x_continuous(labels = percent, limits = c(0, 1.05), expand = c(0, 0)) +
  scale_y_continuous(labels = percent, limits = c(0, 1.05), expand = c(0, 0)) +
  scale_size_continuous(name = "Total devices", range = c(3, 10)) +
  labs(
    title    = "Energy system functionality vs. device functionality",
    subtitle = "Each point = one health facility; size = total devices surveyed",
    x = "% energy systems fully functional",
    y = "% devices fully functional"
  ) +
  theme_eth()

ggsave(file.path(plots_path, "Overview_Energy_vs_Device_Functionality.png"),
       p_overview, width = 10, height = 7)
p_overview
```

# Cross-Analysis

## Row {.tabset}

### Energy source diversity vs. device functionality

```{r}
#| title: "Energy source diversity vs. device functionality"

p_diversity <- combined |>
  filter(!is.na(simpson_funder_dev)) |>
  ggplot(aes(x = simpson_funder_dev, y = pct_dev_functional)) +
  geom_smooth(method = "lm", se = TRUE, colour = eth_blue,
              fill = eth_light, alpha = 0.15, linewidth = 0.8) +
  geom_point(aes(colour = pct_functional, size = n_devices_total), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 2.8,
                  colour = "grey35", max.overlaps = 12) +
  scale_colour_viridis_c(labels = percent, name = "Energy\nfunctionality",
                         option = "D", direction = 1) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_size_continuous(range = c(3, 9), name = "Devices") +
  labs(
    title    = "Device funder diversity vs. device functionality",
    subtitle = "Simpson diversity index of device funders per facility",
    x = "Device funder diversity (Simpson index)",
    y = "% devices fully functional"
  ) +
  theme_eth()

ggsave(file.path(plots_path, "Cross_Device_Funder_Diversity_vs_Functionality.png"),
       p_diversity, width = 9, height = 6)
p_diversity
```

### Funder fragmentation: energy vs. devices

```{r}
#| title: "Funder fragmentation: energy vs. devices"

p_funder_frag <- combined |>
  ggplot(aes(x = n_funders_energy, y = n_funders_devices)) +
  geom_smooth(method = "lm", se = TRUE, colour = eth_blue,
              fill = eth_light, alpha = 0.15, linewidth = 0.8) +
  geom_point(aes(colour = pct_dev_functional, size = n_devices_total), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 3,
                  colour = "grey30", max.overlaps = 15) +
  scale_colour_viridis_c(labels = percent, name = "Device\nfunctionality",
                         option = "D", direction = 1) +
  scale_size_continuous(range = c(3, 9), name = "Devices") +
  labs(
    title    = "Funder fragmentation: energy systems vs. medical devices",
    subtitle = "Facilities fragmented in energy funding tend to be fragmented in device funding too",
    x = "Number of distinct energy funders",
    y = "Number of distinct device funders"
  ) +
  theme_eth()

ggsave(file.path(plots_path, "Cross_Funder_Fragmentation_Energy_vs_Devices.png"),
       p_funder_frag, width = 9, height = 6)
p_funder_frag
```

### Energy system age vs. device delivery year

```{r}
#| title: "Energy system age vs. device delivery year"

p_age <- combined |>
  filter(!is.na(mean_install_year), !is.na(mean_delivery_year)) |>
  ggplot(aes(x = mean_install_year, y = mean_delivery_year)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey60", linewidth = 0.6) +
  geom_point(aes(colour = pct_dev_functional, size = n_devices_total), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 3,
                  colour = "grey30", max.overlaps = 15) +
  scale_colour_viridis_c(labels = percent, name = "Device\nfunctionality",
                         option = "D", direction = 1) +
  scale_size_continuous(range = c(3, 9), name = "Devices") +
  labs(
    title    = "Mean energy system installation year vs. mean device delivery year",
    subtitle = "Points above the diagonal received devices after energy infrastructure; dashed line = simultaneous",
    x = "Mean installation year of energy systems",
    y = "Mean delivery year of medical devices"
  ) +
  theme_eth()

ggsave(file.path(plots_path, "Cross_Energy_Age_vs_Device_Delivery_Year.png"),
       p_age, width = 9, height = 6)
p_age
```

### Facility summary table

```{r}
#| title: "Facility summary table"

combined |>
  select(
    facility_id, facility_name, district,
    n_systems, pct_functional,
    n_devices_total, pct_dev_functional, pct_dysfunctional,
    n_energy_sources, n_funders_energy, n_funders_devices,
    avg_nights_no_light
  ) |>
  arrange(facility_id) |>
  gt() |>
  tab_header(
    title    = "Facility-level summary: energy systems & medical devices",
    subtitle = "Combined from energy-systems-database and med-dev-database"
  ) |>
  cols_label(
    facility_id         = "ID",
    facility_name       = "Facility",
    district            = "District",
    n_systems           = "Energy systems",
    pct_functional      = "% functional (energy)",
    n_devices_total     = "Devices",
    pct_dev_functional  = "% functional (devices)",
    pct_dysfunctional   = "% dysfunctional",
    n_energy_sources    = "Energy sources",
    n_funders_energy    = "Energy funders",
    n_funders_devices   = "Device funders",
    avg_nights_no_light = "Dark nights/mo"
  ) |>
  fmt_percent(columns = c(pct_functional, pct_dev_functional,
                           pct_dysfunctional), decimals = 0) |>
  fmt_number(columns = avg_nights_no_light, decimals = 1) |>
  data_color(columns = pct_functional,
             palette = c(clr_no, "#FFF3CD", clr_yes)) |>
  data_color(columns = pct_dev_functional,
             palette = c(clr_no, "#FFF3CD", clr_yes)) |>
  tab_options(
    table.border.top.color             = eth_blue,
    table.border.bottom.color          = eth_blue,
    column_labels.border.top.color    = eth_light,
    column_labels.border.bottom.color = eth_light
  )
```

# Donor Governance

## Row {.tabset}

### Correlation Table

```{r}
#| title: "Co-funding vs. Outcomes"

safe_cor <- function(x, y) {
  d <- data.frame(x, y) |> filter(!is.na(x), !is.na(y))
  if (nrow(d) < 3) return(tibble(estimate = NA_real_, p.value = NA_real_))
  tidy(cor.test(d$x, d$y, method = "spearman")) |> select(estimate, p.value)
}

outcome_groups <- list(
  "Functionality"  = c("Energy non-functionality"  = "prop_energy_nonfunc",
                       "Device non-functionality"   = "prop_device_nonfunc"),
  "Maintenance"    = c("Repair success rate"        = "pct_repair_success",
                       "Preventive maintenance"     = "pm_score"),
  "Age"            = c("Mean energy install year"   = "mean_install_year",
                       "Mean device delivery year"  = "mean_delivery_year")
)

cor_gov <- purrr::imap_dfr(outcome_groups, function(outcomes, group) {
  purrr::imap_dfr(outcomes, function(col, label) {
    bind_rows(
      safe_cor(df_gov$n_shared,         df_gov[[col]]) |>
        mutate(measure = "Shared funders (count)",       outcome = label, group = group),
      safe_cor(df_gov$jaccard,           df_gov[[col]]) |>
        mutate(measure = "Funder overlap (Jaccard)",     outcome = label, group = group),
      safe_cor(df_gov$simpson_combined,  df_gov[[col]]) |>
        mutate(measure = "Funder fragmentation (Simpson)", outcome = label, group = group)
    )
  })
}) |>
  rename(rho = estimate)

tbl_gov <- cor_gov |>
  select(group, outcome, measure, rho, p.value) |>
  gt(groupname_col = "group") |>
  fmt_number(columns = c(rho, p.value), decimals = 3) |>
  sub_missing(columns = c("rho", "p.value"), missing_text = "—") |>
  cols_label(
    outcome = "Outcome",
    measure = "Co-funding measure",
    rho     = "ρ (Spearman)",
    p.value = "p-value"
  ) |>
  tab_header(
    title    = "Spearman Correlation: Donor Funding vs. Asset Outcomes",
    subtitle = "Rows highlighted yellow: p < 0.05"
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = !is.na(p.value) & p.value < 0.05)
  ) |>
  opt_stylize(style = 1)

tbl_gov
gtsave(tbl_gov, file.path(plots_path, "Donor_Governance_Correlation.html"))
```

### Co-funding vs. Functionality

```{r}
#| title: "Co-funding vs. Functionality"

plot_gov_scatter <- function(data, y_var, y_lab, title) {
  ggplot(data, aes(x = n_shared, y = .data[[y_var]],
                   colour = region, label = facility_name)) +
    geom_smooth(method = "lm", se = TRUE,
                colour = "grey40", linetype = "dashed", linewidth = 0.7) +
    geom_point(size = 4, alpha = 0.8) +
    geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
    scale_x_continuous(breaks = 0:10) +
    scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
    scale_colour_viridis_d(option = "D", name = "Region") +
    labs(
      title = title,
      x     = "Number of shared funders (energy & devices)",
      y     = y_lab
    ) +
    theme_eth()
}

pg1 <- plot_gov_scatter(
  df_gov, "prop_energy_nonfunc",
  "Proportion of energy systems non-functional",
  "Donor co-funding vs. energy non-functionality"
)

pg2 <- plot_gov_scatter(
  df_gov, "prop_device_nonfunc",
  "Proportion of devices dysfunctional",
  "Donor co-funding vs. device non-functionality"
)

p_gov_scatter <- (pg1 / pg2) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p_gov_scatter
ggsave(file.path(plots_path, "Donor_Governance_Scatter.png"),
       p_gov_scatter, width = 10, height = 12)
```

### Per-facility Funder Profile

```{r}
#| title: "Per-facility Funder Profile"

fac_levels <- funder_overlap_wide |>
  left_join(combined |> select(facility_id, facility_name), by = "facility_id") |>
  arrange(n_shared, n_energy_only) |>
  pull(facility_name)

funder_profile <- funder_overlap_wide |>
  left_join(combined |> select(facility_id, facility_name), by = "facility_id") |>
  select(facility_id, facility_name, n_energy_only, n_shared, n_device_only) |>
  pivot_longer(
    cols      = c(n_energy_only, n_shared, n_device_only),
    names_to  = "category",
    values_to = "n_funders"
  ) |>
  mutate(
    facility_name = factor(facility_name, levels = fac_levels),
    category = factor(
      category,
      levels = c("n_energy_only", "n_shared", "n_device_only"),
      labels = c("Energy only", "Shared", "Devices only")
    )
  )

p_funder_profile <- ggplot(funder_profile,
       aes(x = n_funders, y = facility_name, fill = category)) +
  geom_col(position = "stack") +
  scale_fill_manual(
    values = c("Energy only" = eth_light, "Shared" = clr_yes, "Devices only" = clr_part),
    name   = "Funder type"
  ) +
  labs(
    title    = "Per-facility funder profile: energy vs. device funding",
    subtitle = "Facilities ordered by number of shared funders (bottom = most integrated)",
    x        = "Number of distinct funders",
    y        = NULL
  ) +
  theme_eth() +
  theme(legend.position = "bottom")

p_funder_profile
ggsave(file.path(plots_path, "Donor_Governance_Funder_Profile.png"),
       p_funder_profile, width = 9, height = 7)
```

### Co-funding vs. Maintenance

```{r}
#| title: "Co-funding vs. Maintenance"

pm1 <- ggplot(df_gov |> filter(!is.na(pct_repair_success)),
              aes(x = n_shared, y = pct_repair_success,
                  colour = region, label = facility_name)) +
  geom_smooth(method = "lm", se = TRUE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_jitter(size = 4, alpha = 0.8, width = 0.08, height = 0) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(
    title = "Co-funding vs. energy repair success rate",
    x     = "Number of shared funders (energy & devices)",
    y     = "Proportion of repairs successful (energy systems)"
  ) +
  theme_eth()

pm2 <- ggplot(df_gov |> filter(!is.na(pm_score)),
              aes(x = n_shared, y = pm_score,
                  colour = region, label = facility_name)) +
  geom_smooth(method = "lm", se = TRUE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_jitter(size = 4, alpha = 0.8, width = 0.08, height = 0.02) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(
    breaks = c(0, 0.5, 1),
    labels = c("Never", "Sometimes", "Routinely"),
    limits = c(-0.1, 1.1)
  ) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(
    title = "Co-funding vs. preventive maintenance practice",
    x     = "Number of shared funders (energy & devices)",
    y     = "Preventive maintenance (facility self-report)"
  ) +
  theme_eth()

p_gov_maint <- (pm1 / pm2) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p_gov_maint
ggsave(file.path(plots_path, "Donor_Governance_Maintenance.png"),
       p_gov_maint, width = 10, height = 12)
```

### Co-funding vs. Age

```{r}
#| title: "Co-funding vs. System & Device Age"

pa1 <- ggplot(df_gov |> filter(!is.na(mean_install_year)),
              aes(x = n_shared, y = mean_install_year,
                  colour = region, label = facility_name)) +
  geom_smooth(method = "lm", se = TRUE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_point(size = 4, alpha = 0.8) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_x_continuous(breaks = 0:10) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(
    title = "Co-funding vs. mean energy system installation year",
    x     = "Number of shared funders (energy & devices)",
    y     = "Mean installation year (energy systems)"
  ) +
  theme_eth()

pa2 <- ggplot(df_gov |> filter(!is.na(mean_delivery_year)),
              aes(x = n_shared, y = mean_delivery_year,
                  colour = region, label = facility_name)) +
  geom_smooth(method = "lm", se = TRUE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_point(size = 4, alpha = 0.8) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_x_continuous(breaks = 0:10) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(
    title = "Co-funding vs. mean device delivery year",
    x     = "Number of shared funders (energy & devices)",
    y     = "Mean delivery year (medical devices)"
  ) +
  theme_eth()

p_gov_age <- (pa1 / pa2) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p_gov_age
ggsave(file.path(plots_path, "Donor_Governance_Age.png"),
       p_gov_age, width = 10, height = 12)
```

### Funding Alignment (Jaccard)

```{r}
#| title: "Funding Alignment (Jaccard)"

# Reusable helper: scatter with continuous x-axis
plot_gov_cont <- function(data, x_var, x_lab, y_var, y_lab, title,
                          y_is_year = FALSE) {
  p <- ggplot(data |> filter(!is.na(.data[[x_var]]), !is.na(.data[[y_var]])),
              aes(x = .data[[x_var]], y = .data[[y_var]],
                  colour = region, label = facility_name)) +
    geom_smooth(method = "lm", se = TRUE,
                colour = "grey40", linetype = "dashed", linewidth = 0.7) +
    geom_point(size = 3.5, alpha = 0.8) +
    geom_text_repel(size = 2.6, max.overlaps = 15, colour = "grey30") +
    scale_colour_viridis_d(option = "D", name = "Region") +
    labs(title = title, x = x_lab, y = y_lab) +
    theme_eth()
  if (!y_is_year)
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 1),
                                limits = c(0, 1))
  p
}

jac_x  <- "jaccard"
jac_xl <- "Funder overlap — Jaccard similarity (energy ∩ devices / energy ∪ devices)"

jal1 <- plot_gov_cont(df_gov, jac_x, jac_xl,
  "prop_energy_nonfunc", "Energy systems non-functional (%)",
  "Funder alignment vs. energy non-functionality")

jal2 <- plot_gov_cont(df_gov, jac_x, jac_xl,
  "prop_device_nonfunc", "Devices dysfunctional (%)",
  "Funder alignment vs. device non-functionality")

jal3 <- plot_gov_cont(df_gov |> filter(!is.na(pct_repair_success)),
  jac_x, jac_xl,
  "pct_repair_success", "Repairs successful (%)",
  "Funder alignment vs. energy repair success")

jal4 <- ggplot(df_gov |> filter(!is.na(jaccard), !is.na(pm_score)),
               aes(x = jaccard, y = pm_score, colour = region,
                   label = facility_name)) +
  geom_smooth(method = "lm", se = TRUE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_jitter(size = 3.5, alpha = 0.8, width = 0.01, height = 0.02) +
  geom_text_repel(size = 2.6, max.overlaps = 15, colour = "grey30") +
  scale_y_continuous(breaks = c(0, 0.5, 1),
                     labels = c("Never", "Sometimes", "Routinely"),
                     limits = c(-0.1, 1.1)) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(title = "Funder alignment vs. preventive maintenance",
       x = jac_xl, y = "Preventive maintenance") +
  theme_eth()

jal5 <- plot_gov_cont(df_gov |> filter(!is.na(mean_install_year)),
  jac_x, jac_xl,
  "mean_install_year", "Mean installation year (energy)",
  "Funder alignment vs. energy system age", y_is_year = TRUE)

jal6 <- plot_gov_cont(df_gov |> filter(!is.na(mean_delivery_year)),
  jac_x, jac_xl,
  "mean_delivery_year", "Mean delivery year (devices)",
  "Funder alignment vs. device age", y_is_year = TRUE)

p_jac <- (jal1 | jal2) / (jal3 | jal4) / (jal5 | jal6) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p_jac
ggsave(file.path(plots_path, "Donor_Governance_Jaccard.png"),
       p_jac, width = 14, height = 18)
```

### Funder Fragmentation (Simpson)

```{r}
#| title: "Funder Fragmentation (Simpson)"

sim_x  <- "simpson_combined"
sim_xl <- "Funder portfolio fragmentation — Simpson diversity (energy + devices pooled)"

sil1 <- plot_gov_cont(df_gov, sim_x, sim_xl,
  "prop_energy_nonfunc", "Energy systems non-functional (%)",
  "Funder fragmentation vs. energy non-functionality")

sil2 <- plot_gov_cont(df_gov, sim_x, sim_xl,
  "prop_device_nonfunc", "Devices dysfunctional (%)",
  "Funder fragmentation vs. device non-functionality")

sil3 <- plot_gov_cont(df_gov |> filter(!is.na(pct_repair_success)),
  sim_x, sim_xl,
  "pct_repair_success", "Repairs successful (%)",
  "Funder fragmentation vs. energy repair success")

sil4 <- ggplot(df_gov |> filter(!is.na(simpson_combined), !is.na(pm_score)),
               aes(x = simpson_combined, y = pm_score, colour = region,
                   label = facility_name)) +
  geom_smooth(method = "lm", se = TRUE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_jitter(size = 3.5, alpha = 0.8, width = 0.005, height = 0.02) +
  geom_text_repel(size = 2.6, max.overlaps = 15, colour = "grey30") +
  scale_y_continuous(breaks = c(0, 0.5, 1),
                     labels = c("Never", "Sometimes", "Routinely"),
                     limits = c(-0.1, 1.1)) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(title = "Funder fragmentation vs. preventive maintenance",
       x = sim_xl, y = "Preventive maintenance") +
  theme_eth()

sil5 <- plot_gov_cont(df_gov |> filter(!is.na(mean_install_year)),
  sim_x, sim_xl,
  "mean_install_year", "Mean installation year (energy)",
  "Funder fragmentation vs. energy system age", y_is_year = TRUE)

sil6 <- plot_gov_cont(df_gov |> filter(!is.na(mean_delivery_year)),
  sim_x, sim_xl,
  "mean_delivery_year", "Mean delivery year (devices)",
  "Funder fragmentation vs. device age", y_is_year = TRUE)

p_sim <- (sil1 | sil2) / (sil3 | sil4) / (sil5 | sil6) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p_sim
ggsave(file.path(plots_path, "Donor_Governance_Simpson.png"),
       p_sim, width = 14, height = 18)
```
