---
title: "Energy Systems & Medical Devices"
author: "Gian Teufen"
format:
  dashboard:
    nav-buttons: []
---

```{r setup}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(ggplot2)
library(patchwork)
library(gt)
library(ggrepel)
library(scales)
library(broom)

# ── Paths ─────────────────────────────────────────────────────────────────────
proj_root         <- normalizePath(file.path(getwd(), "../.."))
energy_data_path  <- file.path(proj_root, "data/derived_data")
devices_data_path <- "/home/teufeng/med-dev-database/data/derived_data"

plots_path <- file.path(energy_data_path, "plots/energy_and_devices")
dir.create(plots_path, showWarnings = FALSE, recursive = TRUE)

# ── Load data ─────────────────────────────────────────────────────────────────
energy_raw  <- read_rds(file.path(energy_data_path, "Combined_Questionnaire_Systems.rds"))
devices_raw <- read_rds(file.path(devices_data_path, "df_ana.rds"))

energy_raw  <- energy_raw  |> mutate(facility_id = as.integer(facility_id))
devices_raw <- devices_raw |> mutate(facility_id = as.integer(facility_id))

# ── Facility-level energy summary ─────────────────────────────────────────────
energy_fac <- energy_raw |>
  group_by(facility_id, facility_name = facility_name_energy, district, region) |>
  summarise(
    n_systems        = n(),
    n_functional     = sum(functional_now == "Yes",        na.rm = TRUE),
    n_partial        = sum(functional_now == "Partially",  na.rm = TRUE),
    n_nonfunctional  = sum(functional_now == "No",         na.rm = TRUE),
    pct_functional   = n_functional / n_systems,
    has_solar        = any(str_detect(type, "Solar"),      na.rm = TRUE),
    has_grid         = any(type == "Grid",                 na.rm = TRUE),
    has_generator    = any(type == "Generator",            na.rm = TRUE),
    n_energy_sources = sum(c(has_solar, has_grid, has_generator)),
    avg_nights_no_light = first(na.omit(night_treatments_in_darkness_monthly)),
    n_funders_energy = n_distinct(funding[!is.na(funding)]),
    mean_install_year = {
      yrs <- suppressWarnings(as.numeric(installation_year))
      yrs <- yrs[!is.na(yrs) & yrs > 2000]
      if (length(yrs) > 0) mean(yrs) else NA_real_
    },
    .groups = "drop"
  )

# ── Facility-level device summary ─────────────────────────────────────────────
devices_fac <- devices_raw |>
  filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
  group_by(facility_id) |>
  summarise(
    n_devices_total    = n(),
    n_fully_functional = sum(functionality == "fully functional",  na.rm = TRUE),
    n_dysfunctional    = sum(functionality == "dysfunctional",     na.rm = TRUE),
    n_partial_dev      = sum(functionality == "partly functional", na.rm = TRUE),
    pct_dev_functional = n_fully_functional / n_devices_total,
    pct_dysfunctional  = n_dysfunctional    / n_devices_total,
    n_med_devices      = sum(supercategory == "Medical Devices"),
    pct_med_functional = sum(supercategory == "Medical Devices" &
                               functionality == "fully functional", na.rm = TRUE) /
                         pmax(sum(supercategory == "Medical Devices"), 1),
    # Share of devices that need electricity (AC or DC)
    n_powered          = sum(supercategory == "Medical Devices" &
                               power_type %in% c("AC", "DC", "both"), na.rm = TRUE),
    pct_powered        = n_powered / pmax(n_med_devices, 1),
    n_funders_devices  = n_distinct(funding_primary[
      !is.na(funding_primary) &
        !funding_primary %in% c("not applicable", "unknown")]),
    simpson_funder_dev = {
      f <- funding_primary[!is.na(funding_primary) &
                             !funding_primary %in% c("not applicable", "unknown")]
      if (length(f) == 0) NA_real_
      else { p <- table(f) / length(f); 1 - sum(p^2) }
    },
    mean_delivery_year = {
      yrs <- suppressWarnings(as.numeric(year_delivered))
      yrs <- yrs[!is.na(yrs) & yrs > 2000]
      if (length(yrs) > 0) mean(yrs) else NA_real_
    },
    .groups = "drop"
  )

# ── Combined ──────────────────────────────────────────────────────────────────
combined <- inner_join(energy_fac, devices_fac, by = "facility_id") |>
  arrange(facility_id)

# ── Funder overlap (Donor Governance analysis) ────────────────────────────────
norm_funder <- function(x) {
  x_lc <- str_trim(str_to_lower(as.character(x)))
  case_when(
    is.na(x) | x_lc == ""                                              ~ NA_character_,
    x_lc %in% c("moh", "staff", "egpaf", "gov", "government", "dho")  ~ "gov",
    x_lc %in% c("na", "n/a", "not applicable", "unknown")             ~ NA_character_,
    TRUE                                                                ~ x_lc
  )
}

energy_funder_sets <- energy_raw |>
  mutate(funder = norm_funder(funding)) |>
  filter(!is.na(funder)) |>
  group_by(facility_id) |>
  summarise(funders_e = list(sort(unique(funder))), .groups = "drop")

device_funder_sets <- devices_raw |>
  filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
  mutate(funder = norm_funder(funding_primary)) |>
  filter(!is.na(funder)) |>
  group_by(facility_id) |>
  summarise(funders_d = list(sort(unique(funder))), .groups = "drop")

funder_overlap_wide <- energy_funder_sets |>
  inner_join(device_funder_sets, by = "facility_id") |>
  mutate(
    n_shared     = map2_int(funders_e, funders_d, \(e, d) length(intersect(e, d))),
    n_union      = map2_int(funders_e, funders_d, \(e, d) length(union(e, d))),
    n_energy_only = map2_int(funders_e, funders_d, \(e, d) length(setdiff(e, d))),
    n_device_only = map2_int(funders_e, funders_d, \(e, d) length(setdiff(d, e))),
    jaccard      = if_else(n_union > 0, n_shared / n_union, NA_real_),
    is_co_funded = n_shared > 0
  )

energy_repair <- energy_raw |>
  filter(!is.na(repair_success)) |>
  group_by(facility_id) |>
  summarise(
    pct_repair_success = mean(repair_success == "Yes", na.rm = TRUE),
    n_repairs          = n(),
    .groups = "drop"
  )

energy_pm <- energy_raw |>
  group_by(facility_id) |>
  summarise(
    pm_raw = na.omit(preventive_maintenance_carried_out)[1],
    .groups = "drop"
  ) |>
  mutate(
    pm_score = case_when(
      pm_raw == "Routinely"                   ~ 1,
      pm_raw == "Sometimes but not routinely" ~ 0.5,
      pm_raw == "Never"                       ~ 0,
      TRUE                                     ~ NA_real_
    )
  ) |>
  select(facility_id, pm_score)

df_gov <- combined |>
  left_join(
    funder_overlap_wide |> select(facility_id, n_shared, jaccard, is_co_funded),
    by = "facility_id"
  ) |>
  left_join(energy_repair, by = "facility_id") |>
  left_join(energy_pm,     by = "facility_id") |>
  mutate(
    prop_energy_nonfunc = 1 - pct_functional,
    prop_device_nonfunc = pct_dysfunctional
  ) |>
  filter(!is.na(n_shared))

# Combined (energy + devices) funder Simpson diversity per facility
funder_pool <- bind_rows(
  energy_raw |>
    mutate(funder = norm_funder(funding)) |>
    filter(!is.na(funder)) |>
    select(facility_id, funder),
  devices_raw |>
    filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
    mutate(funder = norm_funder(funding_primary)) |>
    filter(!is.na(funder)) |>
    select(facility_id, funder)
)

simpson_combined_df <- funder_pool |>
  group_by(facility_id) |>
  summarise(
    simpson_combined = {
      f <- funder
      if (length(f) == 0) NA_real_
      else { p <- table(f) / length(f); as.numeric(1 - sum(p^2)) }
    },
    .groups = "drop"
  )

df_gov <- df_gov |>
  left_join(simpson_combined_df, by = "facility_id")

# ── Helpers ───────────────────────────────────────────────────────────────────
safe_cor <- function(x, y) {
  d <- data.frame(x, y) |> filter(!is.na(x), !is.na(y))
  if (nrow(d) < 3) return(tibble(estimate = NA_real_, p.value = NA_real_))
  tidy(cor.test(d$x, d$y, method = "spearman")) |> select(estimate, p.value)
}

cor_label <- function(x, y) {
  d <- data.frame(x, y) |> filter(!is.na(x), !is.na(y))
  if (nrow(d) < 3) return(NA_character_)
  r <- cor.test(d$x, d$y, method = "spearman")
  p_str <- if (r$p.value < 0.001) "p < 0.001" else sprintf("p = %.3f", r$p.value)
  sprintf("\u03c1 = %+.3f, %s", r$estimate, p_str)
}

cor_annotate <- function(x, y) {
  annotate("text", x = Inf, y = Inf, label = cor_label(x, y),
           hjust = 1.05, vjust = 1.5, size = 3.5,
           colour = "grey30", fontface = "italic")
}

# ── Theme ─────────────────────────────────────────────────────────────────────
eth_blue  <- "#004D80"
eth_light <- "#0076BA"
# Okabe-Ito colorblind-safe palette
clr_yes   <- "#009E73"   # bluish-green
clr_no    <- "#D55E00"   # vermillion
clr_part  <- "#E69F00"   # orange

theme_eth <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title       = element_text(colour = eth_blue, face = "bold", size = 13),
      plot.subtitle    = element_text(colour = "grey40", size = 10),
      axis.title       = element_text(colour = "grey30", size = 10),
      panel.grid.minor = element_blank()
    )
}
```

# Overview

## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Facilities"
list(icon = "hospital", color = "primary", value = nrow(combined))
```

```{r}
#| content: valuebox
#| title: "Energy systems surveyed"
list(icon = "lightning-charge", color = "info", value = sum(energy_fac$n_systems))
```

```{r}
#| content: valuebox
#| title: "Medical & support devices"
list(icon = "cpu", color = "secondary", value = sum(devices_fac$n_devices_total))
```

```{r}
#| content: valuebox
#| title: "Facilities ≥1 functional energy system"
list(icon = "check-circle", color = "success", value = sum(combined$n_functional >= 1))
```

# Cross-Analysis

## Row {.tabset}

### Energy vs. Device Functionality

```{r}
#| title: "Energy vs. device functionality"

p_overview <- combined |>
  ggplot(aes(x = pct_functional, y = pct_dev_functional)) +
  geom_smooth(method = "lm", se = FALSE, colour = eth_blue,
              fill = eth_light, alpha = 0.15, linewidth = 0.8) +
  geom_point(aes(size = n_devices_total, colour = pct_functional), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 3,
                  colour = "grey30", max.overlaps = 20) +
  scale_colour_viridis_c(labels = percent, name = "Energy\nfunctionality",
                         option = "D", direction = 1) +
  scale_x_continuous(labels = percent, limits = c(0, 1.05), expand = c(0, 0)) +
  scale_y_continuous(labels = percent, limits = c(0, 1.05), expand = c(0, 0)) +
  scale_size_continuous(name = "Total devices", range = c(3, 10)) +
  labs(
    title    = "Energy system functionality vs. device functionality",
    subtitle = "Each point = one health facility; size = total devices surveyed",
    x = "% energy systems fully functional",
    y = "% devices fully functional"
  ) +
  cor_annotate(combined$pct_functional, combined$pct_dev_functional) +
  theme_eth()

ggsave(file.path(plots_path, "Overview_Energy_vs_Device_Functionality.png"),
       p_overview, width = 10, height = 7)
p_overview
```

### Funder fragmentation: energy vs. devices

```{r}
#| title: "Funder fragmentation: energy vs. devices"

p_funder_frag <- combined |>
  ggplot(aes(x = n_funders_energy, y = n_funders_devices)) +
  geom_smooth(method = "lm", se = FALSE, colour = eth_blue,
              fill = eth_light, alpha = 0.15, linewidth = 0.8) +
  geom_point(aes(colour = pct_dev_functional, size = n_devices_total), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 3,
                  colour = "grey30", max.overlaps = 15) +
  scale_colour_viridis_c(labels = percent, name = "Device\nfunctionality",
                         option = "D", direction = 1) +
  scale_size_continuous(range = c(3, 9), name = "Devices") +
  labs(
    title    = "Funder fragmentation: energy systems vs. medical devices",
    subtitle = "Facilities fragmented in energy funding tend to be fragmented in device funding too",
    x = "Number of distinct energy funders",
    y = "Number of distinct device funders"
  ) +
  cor_annotate(combined$n_funders_energy, combined$n_funders_devices) +
  theme_eth()

ggsave(file.path(plots_path, "Cross_Funder_Fragmentation_Energy_vs_Devices.png"),
       p_funder_frag, width = 9, height = 6)
p_funder_frag
```

### Energy system age vs. device delivery year

```{r}
#| title: "Energy system age vs. device delivery year"

p_age <- combined |>
  filter(!is.na(mean_install_year), !is.na(mean_delivery_year)) |>
  ggplot(aes(x = mean_install_year, y = mean_delivery_year)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey60", linewidth = 0.6) +
  geom_point(aes(colour = pct_dev_functional, size = n_devices_total), alpha = 0.85) +
  geom_text_repel(aes(label = facility_name), size = 3,
                  colour = "grey30", max.overlaps = 15) +
  scale_colour_viridis_c(labels = percent, name = "Device\nfunctionality",
                         option = "D", direction = 1) +
  scale_size_continuous(range = c(3, 9), name = "Devices") +
  labs(
    title    = "Mean energy system installation year vs. mean device delivery year",
    subtitle = "Points above the diagonal received devices after energy infrastructure; dashed line = simultaneous",
    x = "Mean installation year of energy systems",
    y = "Mean delivery year of medical devices"
  ) + {
    d <- combined |> filter(!is.na(mean_install_year), !is.na(mean_delivery_year))
    cor_annotate(d$mean_install_year, d$mean_delivery_year)
  } +
  theme_eth()

ggsave(file.path(plots_path, "Cross_Energy_Age_vs_Device_Delivery_Year.png"),
       p_age, width = 9, height = 6)
p_age
```

### Correlation Table

```{r}
#| title: "Cross-dataset correlations"

cross_pairs <- list(
  "Energy–Device Link" = list(
    list(label = "Energy functionality ~ Device functionality",
         x = combined$pct_functional, y = combined$pct_dev_functional)
  ),
  "Funder Structure" = list(
    list(label = "N energy funders ~ N device funders",
         x = combined$n_funders_energy, y = combined$n_funders_devices)
  ),
  "Investment Timing" = list(
    list(label = "Mean energy install year ~ Device delivery year",
         x = combined$mean_install_year, y = combined$mean_delivery_year)
  )
)

cor_cross <- purrr::imap_dfr(cross_pairs, function(pairs, group) {
  purrr::map_dfr(pairs, function(p) {
    safe_cor(p$x, p$y) |>
      mutate(outcome = p$label, group = group)
  })
}) |>
  rename(rho = estimate)

tbl_cross <- cor_cross |>
  select(group, outcome, rho, p.value) |>
  gt(groupname_col = "group") |>
  fmt_number(columns = c(rho, p.value), decimals = 3) |>
  sub_missing(columns = c("rho", "p.value"), missing_text = "—") |>
  cols_label(
    outcome = "Variable pair",
    rho     = "ρ (Spearman)",
    p.value = "p-value"
  ) |>
  tab_header(
    title    = "Spearman Correlation: Cross-dataset associations",
    subtitle = "Rows highlighted yellow: p < 0.05"
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = !is.na(p.value) & p.value < 0.05)
  ) |>
  opt_stylize(style = 1)

tbl_cross
```

### Facility summary table

```{r}
#| title: "Facility summary table"

combined |>
  select(
    facility_id, facility_name, district,
    n_systems, pct_functional,
    n_devices_total, pct_dev_functional, pct_dysfunctional,
    n_energy_sources, n_funders_energy, n_funders_devices,
    avg_nights_no_light
  ) |>
  arrange(facility_id) |>
  gt() |>
  tab_header(
    title    = "Facility-level summary: energy systems & medical devices",
    subtitle = "Combined from energy-systems-database and med-dev-database"
  ) |>
  cols_label(
    facility_id         = "ID",
    facility_name       = "Facility",
    district            = "District",
    n_systems           = "Energy systems",
    pct_functional      = "% functional (energy)",
    n_devices_total     = "Devices",
    pct_dev_functional  = "% functional (devices)",
    pct_dysfunctional   = "% dysfunctional",
    n_energy_sources    = "Energy sources",
    n_funders_energy    = "Energy funders",
    n_funders_devices   = "Device funders",
    avg_nights_no_light = "Dark nights/mo"
  ) |>
  fmt_percent(columns = c(pct_functional, pct_dev_functional,
                           pct_dysfunctional), decimals = 0) |>
  fmt_number(columns = avg_nights_no_light, decimals = 1) |>
  data_color(columns = pct_functional,
             palette = c(clr_no, "#FFF3CD", clr_yes)) |>
  data_color(columns = pct_dev_functional,
             palette = c(clr_no, "#FFF3CD", clr_yes)) |>
  tab_options(
    table.border.top.color             = eth_blue,
    table.border.bottom.color          = eth_blue,
    column_labels.border.top.color    = eth_light,
    column_labels.border.bottom.color = eth_light
  )
```

# Donor Governance

## Row {.tabset}

### Correlation Table

```{r}
#| title: "Co-funding vs. Outcomes"

outcome_groups <- list(
  "Functionality" = c("Energy non-functionality" = "prop_energy_nonfunc",
                      "Device non-functionality"  = "prop_device_nonfunc"),
  "Maintenance"   = c("Preventive maintenance"    = "pm_score")
)

cor_gov <- purrr::imap_dfr(outcome_groups, function(outcomes, group) {
  purrr::imap_dfr(outcomes, function(col, label) {
    bind_rows(
      safe_cor(df_gov$n_shared,         df_gov[[col]]) |>
        mutate(measure = "Shared funders (count)",       outcome = label, group = group),
      safe_cor(df_gov$jaccard,           df_gov[[col]]) |>
        mutate(measure = "Funder overlap (Jaccard)",     outcome = label, group = group)
    )
  })
}) |>
  rename(rho = estimate)

tbl_gov <- cor_gov |>
  select(group, outcome, measure, rho, p.value) |>
  gt(groupname_col = "group") |>
  fmt_number(columns = c(rho, p.value), decimals = 3) |>
  sub_missing(columns = c("rho", "p.value"), missing_text = "—") |>
  cols_label(
    outcome = "Outcome",
    measure = "Co-funding measure",
    rho     = "ρ (Spearman)",
    p.value = "p-value"
  ) |>
  tab_header(
    title    = "Spearman Correlation: Donor Funding vs. Asset Outcomes",
    subtitle = "Rows highlighted yellow: p < 0.05"
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = !is.na(p.value) & p.value < 0.05)
  ) |>
  opt_stylize(style = 1)

tbl_gov
gtsave(tbl_gov, file.path(plots_path, "Donor_Governance_Correlation.html"))
```

### Per-facility Funder Profile

```{r}
#| title: "Per-facility Funder Profile"

fac_levels <- funder_overlap_wide |>
  left_join(combined |> select(facility_id, facility_name), by = "facility_id") |>
  arrange(n_shared, n_energy_only) |>
  pull(facility_name)

funder_profile <- funder_overlap_wide |>
  left_join(combined |> select(facility_id, facility_name), by = "facility_id") |>
  select(facility_id, facility_name, n_energy_only, n_shared, n_device_only) |>
  pivot_longer(
    cols      = c(n_energy_only, n_shared, n_device_only),
    names_to  = "category",
    values_to = "n_funders"
  ) |>
  mutate(
    facility_name = factor(facility_name, levels = fac_levels),
    category = factor(
      category,
      levels = c("n_energy_only", "n_shared", "n_device_only"),
      labels = c("Energy only", "Shared", "Devices only")
    )
  )

p_funder_profile <- ggplot(funder_profile,
       aes(x = n_funders, y = facility_name, fill = category)) +
  geom_col(position = "stack") +
  scale_fill_manual(
    values = c("Energy only" = eth_light, "Shared" = clr_yes, "Devices only" = clr_part),
    name   = "Funder type"
  ) +
  labs(
    title    = "Per-facility funder profile: energy vs. device funding",
    subtitle = "Facilities ordered by number of shared funders (bottom = most integrated)",
    x        = "Number of distinct funders",
    y        = NULL
  ) +
  theme_eth() +
  theme(legend.position = "bottom")

p_funder_profile
ggsave(file.path(plots_path, "Donor_Governance_Funder_Profile.png"),
       p_funder_profile, width = 9, height = 7)
```

### Co-funding vs. Maintenance

```{r}
#| title: "Co-funding vs. Maintenance"

pm2 <- ggplot(df_gov |> filter(!is.na(pm_score)),
              aes(x = n_shared, y = pm_score,
                  colour = region, label = facility_name)) +
  geom_smooth(method = "lm", se = FALSE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_jitter(size = 4, alpha = 0.8, width = 0.08, height = 0.02) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(
    breaks = c(0, 0.5, 1),
    labels = c("Never", "Sometimes", "Routinely"),
    limits = c(-0.1, 1.1)
  ) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(
    title = "Co-funding vs. preventive maintenance practice",
    x     = "Number of shared funders (energy & devices)",
    y     = "Preventive maintenance (facility self-report)"
  ) + {
    d <- df_gov |> filter(!is.na(pm_score))
    annotate("text", x = Inf, y = 1.1, label = cor_label(d$n_shared, d$pm_score),
             hjust = 1.05, vjust = 1.5, size = 3.5, colour = "grey30", fontface = "italic")
  } +
  theme_eth()

p_gov_maint <- pm2 + theme(legend.position = "bottom")

p_gov_maint
ggsave(file.path(plots_path, "Donor_Governance_Maintenance.png"),
       p_gov_maint, width = 10, height = 6)
```

### Funding Alignment (Jaccard)

```{r}
#| output: false

# Reusable helper: scatter with continuous x-axis
plot_gov_cont <- function(data, x_var, x_lab, y_var, y_lab, title,
                          y_is_year = FALSE) {
  p <- ggplot(data |> filter(!is.na(.data[[x_var]]), !is.na(.data[[y_var]])),
              aes(x = .data[[x_var]], y = .data[[y_var]],
                  colour = region, label = facility_name)) +
    geom_smooth(method = "lm", se = FALSE,
                colour = "grey40", linetype = "dashed", linewidth = 0.7) +
    geom_point(size = 3.5, alpha = 0.8) +
    geom_text_repel(size = 2.6, max.overlaps = 15, colour = "grey30") +
    scale_colour_viridis_d(option = "D", name = "Region") +
    labs(title = title, x = x_lab, y = y_lab) +
    theme_eth()
  if (!y_is_year)
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 1),
                                limits = c(0, 1))
  p
}

jac_x  <- "jaccard"
jac_xl <- "Funder overlap — Jaccard similarity (energy ∩ devices / energy ∪ devices)"

jal2 <- plot_gov_cont(df_gov, jac_x, jac_xl,
  "prop_device_nonfunc", "Devices dysfunctional (%)",
  "Funder alignment vs. device non-functionality") +
  cor_annotate(df_gov$jaccard, df_gov$prop_device_nonfunc)

jal4 <- ggplot(df_gov |> filter(!is.na(jaccard), !is.na(pm_score)),
               aes(x = jaccard, y = pm_score, colour = region,
                   label = facility_name)) +
  geom_smooth(method = "lm", se = FALSE,
              colour = "grey40", linetype = "dashed", linewidth = 0.7) +
  geom_jitter(size = 3.5, alpha = 0.8, width = 0.01, height = 0.02) +
  geom_text_repel(size = 2.6, max.overlaps = 15, colour = "grey30") +
  scale_y_continuous(breaks = c(0, 0.5, 1),
                     labels = c("Never", "Sometimes", "Routinely"),
                     limits = c(-0.1, 1.1)) +
  scale_colour_viridis_d(option = "D", name = "Region") +
  labs(title = "Funder alignment vs. preventive maintenance",
       x = jac_xl, y = "Preventive maintenance") + {
    d <- df_gov |> filter(!is.na(jaccard), !is.na(pm_score))
    annotate("text", x = Inf, y = 1.1, label = cor_label(d$jaccard, d$pm_score),
             hjust = 1.05, vjust = 1.5, size = 3.5, colour = "grey30", fontface = "italic")
  } +
  theme_eth()

p_jac <- (jal2 | jal4) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
ggsave(file.path(plots_path, "Donor_Governance_Jaccard.png"),
       p_jac, width = 14, height = 7)
```

::: {.panel-tabset}

#### Device Non-functionality

```{r}
jal2
```

#### Preventive Maintenance

```{r}
jal4
```

:::

# Fragmentation

## Row {.tabset}

### Data & Correlation Table

```{r}
#| title: "Fragmentation: Correlation Table"

# ── Funder diversity (energy systems) ────────────────────────────────────────
funder_diversity_e <- energy_raw |>
  mutate(funder = norm_funder(funding)) |>
  filter(!is.na(funder)) |>
  group_by(facility_id, funder) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(facility_id) |>
  mutate(p_i = n / sum(n)) |>
  summarise(
    n_systems_frag = sum(n),
    n_funders_frag = n_distinct(funder),
    simpson_funder = 1 - sum(p_i^2),
    .groups = "drop"
  )

# ── Manufacturer diversity (energy systems) ───────────────────────────────────
mfr_diversity_e <- energy_raw |>
  mutate(
    component_brand = case_when(
      !is.na(inverter_manufacturer) ~ str_trim(inverter_manufacturer),
      !is.na(brand)                 ~ str_trim(brand),
      TRUE                          ~ NA_character_
    )
  ) |>
  filter(!is.na(component_brand),
         !str_to_lower(component_brand) %in% c("unknown", "n/a", "")) |>
  group_by(facility_id, component_brand) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(facility_id) |>
  mutate(p_i = n / sum(n)) |>
  summarise(
    n_brands    = n_distinct(component_brand),
    simpson_mfr = 1 - sum(p_i^2),
    .groups = "drop"
  )

# ── Non-functionality ratio ───────────────────────────────────────────────────
func_ratio_e <- energy_raw |>
  filter(!is.na(functional_now)) |>
  mutate(
    is_nonfunctional = case_when(
      functional_now == "No"        ~ 1,
      functional_now == "Partially" ~ 0.5,
      functional_now == "Yes"       ~ 0
    )
  ) |>
  group_by(facility_id) |>
  summarise(
    n_systems_total = n(),
    prop_nonfunc    = mean(is_nonfunctional),
    .groups = "drop"
  )

# ── Combined ─────────────────────────────────────────────────────────────────
df_frag <- funder_diversity_e |>
  left_join(mfr_diversity_e, by = "facility_id") |>
  left_join(func_ratio_e,    by = "facility_id") |>
  left_join(
    combined |> select(facility_id, facility_name, region, district, mean_install_year),
    by = "facility_id"
  )

# ── Spearman correlation table ────────────────────────────────────────────────
cor_frag <- bind_rows(
  safe_cor(df_frag$simpson_funder, df_frag$prop_nonfunc) |>
    mutate(measure = "Simpson funder diversity"),
  safe_cor(df_frag$n_funders_frag, df_frag$prop_nonfunc) |>
    mutate(measure = "Number of distinct funders"),
  safe_cor(df_frag$simpson_mfr,    df_frag$prop_nonfunc) |>
    mutate(measure = "Simpson manufacturer diversity")
) |>
  rename(rho = estimate)

tbl_frag <- cor_frag |>
  gt() |>
  fmt_number(columns = c(rho, p.value), decimals = 3) |>
  sub_missing(columns = c("rho", "p.value"), missing_text = "—") |>
  cols_label(measure = "Measure", rho = "ρ (Spearman)", p.value = "p-value") |>
  tab_header(title = "Spearman Correlation: Fragmentation vs. Non-functionality",
             subtitle = "Rows highlighted yellow: p < 0.05") |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = !is.na(p.value) & p.value < 0.05)
  ) |>
  opt_stylize(style = 1)

tbl_frag
gtsave(tbl_frag, file.path(plots_path, "Fragmentation_Correlation.html"))
```

### Fragmentation Scatter

```{r}
#| output: false

plot_frag_scatter <- function(data, x_var, x_lab) {
  ggplot(data, aes(x = .data[[x_var]], y = prop_nonfunc,
                   colour = region, label = facility_name)) +
    geom_smooth(method = "lm", se = FALSE,
                colour = "grey40", linetype = "dashed", linewidth = 0.7) +
    geom_point(size = 4, alpha = 0.8) +
    geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
    scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
    scale_colour_viridis_d(option = "D", name = "Region") +
    labs(x = x_lab, y = "Proportion of non-functional systems") +
    theme_eth()
}

df_frag_mfr <- df_frag |> filter(!is.na(simpson_mfr))

pf1 <- plot_frag_scatter(df_frag, "simpson_funder", "Funder diversity (Simpson index)") +
  cor_annotate(df_frag$simpson_funder, df_frag$prop_nonfunc)
pf2 <- plot_frag_scatter(df_frag, "n_funders_frag", "Number of distinct funders") +
  cor_annotate(df_frag$n_funders_frag, df_frag$prop_nonfunc)
pf3 <- plot_frag_scatter(df_frag_mfr, "simpson_mfr", "Manufacturer diversity (Simpson index)") +
  cor_annotate(df_frag_mfr$simpson_mfr, df_frag_mfr$prop_nonfunc)

p_frag_scatter <- (pf1 / pf2 / pf3) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
ggsave(file.path(plots_path, "Fragmentation_Scatter.png"),
       p_frag_scatter, width = 10, height = 18)
```

::: {.panel-tabset}

#### Funder Diversity (Simpson)

```{r}
pf1 + theme(legend.position = "bottom")
```

#### Number of Funders

```{r}
pf2 + theme(legend.position = "bottom")
```

#### Manufacturer Diversity (Simpson)

```{r}
pf3 + theme(legend.position = "bottom")
```

:::

### Sensitivity: Excl. Outlier

```{r}
#| title: "Sensitivity: Excl. highest non-functionality facility"

outlier_id <- df_frag |>
  filter(!is.na(prop_nonfunc)) |>
  slice_max(prop_nonfunc, n = 1) |>
  pull(facility_id)

outlier_name <- df_frag |>
  filter(facility_id == outlier_id) |>
  pull(facility_name)

df_no_out <- df_frag |> filter(facility_id != outlier_id)

cor_sensitivity <- bind_rows(
  safe_cor(df_no_out$simpson_funder, df_no_out$prop_nonfunc) |>
    mutate(measure = "Simpson funder diversity"),
  safe_cor(df_no_out$n_funders_frag, df_no_out$prop_nonfunc) |>
    mutate(measure = "Number of distinct funders"),
  safe_cor(df_no_out$simpson_mfr,    df_no_out$prop_nonfunc) |>
    mutate(measure = "Simpson manufacturer diversity")
) |>
  rename(rho = estimate)

tbl_sensitivity <- cor_sensitivity |>
  gt() |>
  fmt_number(columns = c(rho, p.value), decimals = 3) |>
  sub_missing(columns = c("rho", "p.value"), missing_text = "—") |>
  cols_label(measure = "Measure", rho = "ρ (Spearman)", p.value = "p-value") |>
  tab_header(
    title    = glue::glue("Sensitivity: Excluding {outlier_name}"),
    subtitle = "Checks whether the highest non-functionality facility drives the correlation"
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = !is.na(p.value) & p.value < 0.05)
  ) |>
  opt_stylize(style = 1)

tbl_sensitivity
```

### Age-Adjusted Correlation

```{r}
#| title: "Age-Adjusted Correlation"

partial_spearman <- function(x, y, z) {
  rx <- residuals(lm(rank(x) ~ rank(z)))
  ry <- residuals(lm(rank(y) ~ rank(z)))
  cor.test(rx, ry, method = "pearson")
}

df_age_frag <- df_frag |> filter(!is.na(mean_install_year))

age_results <- bind_rows(
  tidy(partial_spearman(df_age_frag$simpson_funder, df_age_frag$prop_nonfunc,
                        df_age_frag$mean_install_year)) |>
    mutate(measure = "Simpson funder diversity"),
  tidy(partial_spearman(df_age_frag$n_funders_frag, df_age_frag$prop_nonfunc,
                        df_age_frag$mean_install_year)) |>
    mutate(measure = "Number of distinct funders")
) |>
  select(measure, estimate, p.value) |>
  rename(r_partial = estimate)

tbl_age_frag <- age_results |>
  gt() |>
  fmt_number(columns = c(r_partial, p.value), decimals = 3) |>
  sub_missing(columns = c("r_partial", "p.value"), missing_text = "—") |>
  cols_label(measure = "Measure", r_partial = "Partial r", p.value = "p-value") |>
  tab_header(
    title    = "Partial Correlation: Controlling for Mean Installation Year",
    subtitle = "Tests whether fragmentation predicts non-functionality beyond system age"
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = !is.na(p.value) & p.value < 0.05)
  ) |>
  opt_stylize(style = 1)

tbl_age_frag
```

### Funder Fragmentation Bar Chart

```{r}
#| title: "Funder Fragmentation Bar Chart"

df_bar_frag <- energy_raw |>
  mutate(funder_clean = norm_funder(funding)) |>
  mutate(funder_clean = replace_na(funder_clean, "Unknown")) |>
  left_join(
    df_frag |> select(facility_id, facility_name, simpson_funder),
    by = "facility_id"
  ) |>
  filter(!is.na(simpson_funder)) |>
  mutate(facility_name = fct_reorder(facility_name, simpson_funder))

p_funder_bar <- ggplot(df_bar_frag,
       aes(x = facility_name, fill = fct_infreq(funder_clean))) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  scale_fill_viridis_d(option = "H") +
  labs(
    title    = "Energy system funder composition per facility",
    subtitle = "Ordered by funder diversity — most fragmented at top",
    x        = NULL,
    y        = "Energy system count",
    fill     = "Funder"
  ) +
  theme_eth() +
  theme(legend.position = "bottom")

p_funder_bar
ggsave(file.path(plots_path, "Fragmentation_Bar_Chart.png"),
       p_funder_bar, width = 10, height = 7)
```

# Maintenance Effectiveness

## Row {.tabset}

### Energy Systems

```{r}
#| output: false

# ── Energy: system-level data with maintenance & age ─────────────────────────
energy_maint <- energy_raw |>
  mutate(
    maint_norm = case_when(
      str_to_lower(str_trim(as.character(maintenance_by))) == "no" ~ "None",
      str_to_lower(str_trim(as.character(maintenance_by))) == "dho" ~ "DHO/Gov",
      !is.na(maintenance_by) ~ "Donor/Installer",
      TRUE ~ NA_character_
    ),
    install_yr = suppressWarnings(as.numeric(installation_year)),
    install_yr = if_else(install_yr > 2000 & install_yr <= 2025,
                         install_yr, NA_real_),
    system_age = 2025 - install_yr,
    func_bin   = case_when(
      functional_now == "Yes"       ~ "Functional",
      functional_now == "Partially" ~ "Partial",
      functional_now == "No"        ~ "Non-functional",
      TRUE                           ~ NA_character_
    ),
    func_bin = factor(func_bin, levels = c("Functional", "Partial", "Non-functional"))
  ) |>
  left_join(
    energy_pm |>
      mutate(
        pm_label = case_when(
          pm_score == 1   ~ "Routinely",
          pm_score == 0.5 ~ "Sometimes",
          pm_score == 0   ~ "Never",
          TRUE             ~ NA_character_
        ),
        pm_label = factor(pm_label, levels = c("Never", "Sometimes", "Routinely"))
      ) |>
      select(facility_id, pm_score, pm_label),
    by = "facility_id"
  )

# ── Facility-level: PM label × energy functionality ───────────────────────────
e_pm_fac <- energy_pm |>
  mutate(
    pm_label = case_when(
      pm_score == 1   ~ "Routinely",
      pm_score == 0.5 ~ "Sometimes",
      pm_score == 0   ~ "Never",
      TRUE             ~ NA_character_
    ),
    pm_label = factor(pm_label, levels = c("Never", "Sometimes", "Routinely"))
  ) |>
  inner_join(
    combined |> select(facility_id, facility_name, pct_functional, region,
                       mean_install_year),
    by = "facility_id"
  ) |>
  filter(!is.na(pm_label)) |>
  mutate(mean_fac_age = 2025 - mean_install_year)

# ── E1: PM frequency vs. % functional (facility-level, coloured by mean age) ──
pe1 <- ggplot(e_pm_fac, aes(x = pm_label, y = pct_functional,
                              colour = mean_fac_age, label = facility_name)) +
  geom_boxplot(aes(group = pm_label), outlier.shape = NA,
               fill = "grey92", colour = "grey60", width = 0.45, alpha = 0.6) +
  geom_jitter(size = 4, alpha = 0.85, width = 0.12, height = 0) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_y_continuous(labels = percent, limits = c(0, 1.05)) +
  scale_colour_viridis_c(option = "D", name = "Mean system\nage (yrs)",
                         direction = -1) +
  annotate("text", x = Inf, y = Inf,
           label = cor_label(as.numeric(e_pm_fac$pm_label), e_pm_fac$pct_functional),
           hjust = 1.05, vjust = 1.5, size = 3.5, colour = "grey30",
           fontface = "italic") +
  labs(
    title    = "Preventive maintenance frequency vs. energy system functionality",
    subtitle = "Each point = one facility; colour = mean system age",
    x        = "Preventive maintenance frequency",
    y        = "% energy systems fully functional"
  ) +
  theme_eth()

# ── E1b: PM vs. functionality (system-level, coloured by system age) ──────────
pe1b <- energy_maint |>
  filter(!is.na(pm_label), !is.na(func_bin), !is.na(system_age),
         system_age >= 0, system_age <= 25) |>
  ggplot(aes(x = pm_label, y = func_bin,
             colour = system_age)) +
  geom_jitter(size = 3, alpha = 0.8, width = 0.2, height = 0.18) +
  scale_colour_viridis_c(option = "D", name = "System age\n(years)",
                         direction = -1) +
  scale_y_discrete(limits = rev) +
  labs(
    title    = "Preventive maintenance vs. system functionality (system-level)",
    subtitle = "Each point = one energy system; colour = system age",
    x        = "Preventive maintenance frequency",
    y        = "Functional status"
  ) +
  theme_eth()

# ── E2: Maintenance party vs. functionality (system-level stacked bar) ─────────
pe2 <- energy_maint |>
  filter(!is.na(maint_norm), !is.na(func_bin)) |>
  count(maint_norm, func_bin) |>
  group_by(maint_norm) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = maint_norm, y = pct, fill = func_bin)) +
  geom_col(position = "stack", width = 0.55) +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(
    values = c("Functional" = clr_yes, "Partial" = clr_part,
               "Non-functional" = clr_no),
    name = "Status"
  ) +
  labs(
    title    = "Maintenance responsibility vs. energy system functionality",
    subtitle = "System-level breakdown by who is responsible for maintenance",
    x        = "Maintenance party",
    y        = "Share of energy systems"
  ) +
  theme_eth() +
  theme(legend.position = "bottom")

# ── E3: System age by PM level × functional status ────────────────────────────
pe3 <- energy_maint |>
  filter(!is.na(pm_label), !is.na(system_age),
         system_age >= 0, system_age <= 25,
         !is.na(func_bin)) |>
  ggplot(aes(x = pm_label, y = system_age, fill = func_bin)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.45,
               position = position_dodge(0.75), width = 0.55) +
  geom_jitter(aes(colour = func_bin),
              position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.75),
              size = 2.5, alpha = 0.8) +
  scale_fill_manual(
    values = c("Functional" = clr_yes, "Partial" = clr_part,
               "Non-functional" = clr_no),
    name = "Status"
  ) +
  scale_colour_manual(
    values = c("Functional" = clr_yes, "Partial" = clr_part,
               "Non-functional" = clr_no),
    guide = "none"
  ) +
  labs(
    title    = "System age by PM frequency and functional status",
    subtitle = "Do routinely maintained systems remain functional at greater age?",
    x        = "Preventive maintenance frequency",
    y        = "System age (years since installation)"
  ) +
  theme_eth() +
  theme(legend.position = "bottom")
```

::: {.panel-tabset}

#### PM vs. Functionality (Facility)

```{r}
pe1 + theme(legend.position = "bottom")
```

#### PM vs. Functionality (System)

```{r}
pe1b + theme(legend.position = "bottom")
```

#### Maintenance Party

```{r}
pe2
```

#### System Longevity

```{r}
pe3
```

:::

### Medical Devices

```{r}
#| output: false

# ── Devices: device-level maintenance & age data ──────────────────────────────
devices_maint <- devices_raw |>
  filter(supercategory %in% c("Medical Devices", "ICT & Electronics", "Utilities")) |>
  mutate(
    maint_norm_dev = case_when(
      maintenance_primary == "DHO/MoH/Govt" ~ "DHO/Gov",
      maintenance_primary == "unknown"       ~ NA_character_,
      !is.na(maintenance_primary)             ~ "Donor/Installer",
      TRUE                                    ~ NA_character_
    ),
    deliv_yr   = suppressWarnings(as.numeric(year_delivered)),
    deliv_yr   = if_else(deliv_yr > 2000 & deliv_yr <= 2025, deliv_yr, NA_real_),
    device_age = 2025 - deliv_yr,
    pm_dev     = case_when(
      has_preventive_maintenance == "Routinely"                   ~ "Routinely",
      has_preventive_maintenance == "Sometimes but not routinely" ~ "Sometimes",
      has_preventive_maintenance == "Never"                       ~ "Never",
      TRUE                                                         ~ NA_character_
    ),
    pm_dev   = factor(pm_dev, levels = c("Never", "Sometimes", "Routinely")),
    func_dev = case_when(
      functionality == "fully functional"  ~ "Functional",
      functionality == "partly functional" ~ "Partial",
      functionality == "dysfunctional"     ~ "Non-functional",
      TRUE                                  ~ NA_character_
    ),
    func_dev = factor(func_dev, levels = c("Functional", "Partial", "Non-functional"))
  )

# ── Facility-level: dominant PM × device functionality ────────────────────────
dev_pm_fac <- devices_maint |>
  group_by(facility_id) |>
  summarise(
    pm_dominant = {
      vals <- pm_dev[!is.na(pm_dev)]
      if (length(vals) == 0) NA_character_
      else as.character(names(sort(table(vals), decreasing = TRUE))[1])
    },
    pct_dev_func  = mean(functionality == "fully functional", na.rm = TRUE),
    mean_dev_age  = mean(device_age[!is.na(device_age) & device_age >= 0 &
                                      device_age <= 20], na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    pm_dominant = factor(pm_dominant, levels = c("Never", "Sometimes", "Routinely"))
  ) |>
  left_join(combined |> select(facility_id, facility_name, region),
            by = "facility_id") |>
  filter(!is.na(pm_dominant))

# ── D1: PM frequency vs. % functional devices (facility-level, coloured by mean age) ─
pd1 <- ggplot(dev_pm_fac, aes(x = pm_dominant, y = pct_dev_func,
                                colour = mean_dev_age, label = facility_name)) +
  geom_boxplot(aes(group = pm_dominant), outlier.shape = NA,
               fill = "grey92", colour = "grey60", width = 0.45, alpha = 0.6) +
  geom_jitter(size = 4, alpha = 0.85, width = 0.12, height = 0) +
  geom_text_repel(size = 2.8, max.overlaps = 15, colour = "grey30") +
  scale_y_continuous(labels = percent, limits = c(0, 1.05)) +
  scale_colour_viridis_c(option = "D", name = "Mean device\nage (yrs)",
                         direction = -1) +
  annotate("text", x = Inf, y = Inf,
           label = cor_label(as.numeric(dev_pm_fac$pm_dominant),
                             dev_pm_fac$pct_dev_func),
           hjust = 1.05, vjust = 1.5, size = 3.5, colour = "grey30",
           fontface = "italic") +
  labs(
    title    = "Preventive maintenance frequency vs. device functionality",
    subtitle = "Each point = one facility; colour = mean device age",
    x        = "Preventive maintenance frequency (dominant at facility)",
    y        = "% devices fully functional"
  ) +
  theme_eth()

# ── D1b: PM vs. functionality (device-level, coloured by device age) ──────────
pd1b <- devices_maint |>
  filter(!is.na(pm_dev), !is.na(func_dev), !is.na(device_age),
         device_age >= 0, device_age <= 20) |>
  ggplot(aes(x = pm_dev, y = func_dev, colour = device_age)) +
  geom_jitter(size = 1.8, alpha = 0.55, width = 0.2, height = 0.18) +
  scale_colour_viridis_c(option = "D", name = "Device age\n(years)",
                         direction = -1) +
  scale_y_discrete(limits = rev) +
  labs(
    title    = "Preventive maintenance vs. device functionality (device-level)",
    subtitle = "Each point = one device; colour = device age",
    x        = "Preventive maintenance frequency",
    y        = "Functional status"
  ) +
  theme_eth()

# ── D2: Maintenance party vs. functionality (device-level stacked bar) ─────────
pd2 <- devices_maint |>
  filter(!is.na(maint_norm_dev), !is.na(func_dev)) |>
  count(maint_norm_dev, func_dev) |>
  group_by(maint_norm_dev) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = maint_norm_dev, y = pct, fill = func_dev)) +
  geom_col(position = "stack", width = 0.55) +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(
    values = c("Functional" = clr_yes, "Partial" = clr_part,
               "Non-functional" = clr_no),
    name = "Status"
  ) +
  labs(
    title    = "Maintenance responsibility vs. device functionality",
    subtitle = "Device-level breakdown by who is responsible for maintenance",
    x        = "Maintenance party",
    y        = "Share of devices"
  ) +
  theme_eth() +
  theme(legend.position = "bottom")

# ── D3: Device age by PM level × functional status ────────────────────────────
pd3 <- devices_maint |>
  filter(!is.na(pm_dev), !is.na(device_age),
         device_age >= 0, device_age <= 15,
         func_dev %in% c("Functional", "Non-functional")) |>
  ggplot(aes(x = pm_dev, y = device_age, fill = func_dev)) +
  geom_violin(alpha = 0.35, position = position_dodge(0.8), width = 0.7,
              draw_quantiles = 0.5) +
  geom_jitter(aes(colour = func_dev),
              position = position_jitterdodge(jitter.width = 0.07, dodge.width = 0.8),
              size = 1.2, alpha = 0.35) +
  scale_fill_manual(
    values = c("Functional" = clr_yes, "Non-functional" = clr_no),
    name = "Status"
  ) +
  scale_colour_manual(
    values = c("Functional" = clr_yes, "Non-functional" = clr_no),
    guide  = "none"
  ) +
  labs(
    title    = "Device age by PM frequency and functionality status",
    subtitle = "Do routinely maintained devices remain functional at greater age?",
    x        = "Preventive maintenance frequency",
    y        = "Device age (years since delivery)"
  ) +
  theme_eth() +
  theme(legend.position = "bottom")
```

::: {.panel-tabset}

#### PM vs. Functionality (Facility)

```{r}
pd1 + theme(legend.position = "bottom")
```

#### PM vs. Functionality (Device)

```{r}
pd1b + theme(legend.position = "bottom")
```

#### Maintenance Party

```{r}
pd2
```

#### Device Longevity

```{r}
pd3
```

:::
