---
title: "Electricity Supply"
author: "Gian Teufen"
format: 
  dashboard:
    nav-buttons: []
---

```{r}
#| echo: false

library(tidyverse)
library(dplyr)
library(googlesheets4)
library(readr)
library(hms)
library(scales)
library(ggthemes)
library(forcats)
library(ggplot2)
library(ggExtra)
library(viridis)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(terra)
library(dplyr)
library(spData)
library(spDataLarge)
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(malawi)
library(ggridges)
library(gt) #Presentation-Ready Display Tables
library(gtsummary) #publication-ready analytical and summary tables using the R programming language
library(knitr) #general-purpose tool for dynamic report generation in R using Literate Programming techniques.
library(DT) #Data objects in R can be rendered as HTML tables using the JavaScript library 'DataTables'
library(lubridate) #tools to make dates parsing and manipulation easier
library(kableExtra)
library(patchwork)
library(ggrepel)




# Auto-detect base data path
if (dir.exists("G:/.shortcut-targets-by-id/1R_jaR_bY959F-kVkmoRlCS4npFhRrr4k/2025-msc-thesis-teufeng/data")) {
  base_path <- "G:/.shortcut-targets-by-id/1R_jaR_bY959F-kVkmoRlCS4npFhRrr4k/2025-msc-thesis-teufeng/data"
} else {
  base_path <- "data"
}

df <- read_rds(file.path(base_path, "derived_data/HC_EnergySystems.rds"))

kobo_questionnaire <- read_rds(file.path(base_path, "derived_data/Kobo_Questionnaire.rds"))

combined <- read_rds(file.path(base_path, "derived_data/Combined_Questionnaire_Systems.rds"))
```

# Energy Stacking

<!-- ## Row {height="30%"} -->

<!-- ```{r} -->

<!-- #| content: valuebox -->

<!-- #| title: "Surveyed Facilities" -->

<!-- list( -->

<!--   icon = "bar-chart", -->

<!--   color = "primary", -->

<!--   value = length(unique(df$facility)) -->

<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #| content: valuebox -->

<!-- #| title: "Surveyed Rooms" -->

<!-- list( -->

<!--   icon = "bar-chart", -->

<!--   color = "secondary", -->

<!--   value = nrow(rooms) -->

<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #| content: valuebox -->

<!-- #| title: "Surveyed Devices" -->

<!-- list( -->

<!--   icon = "bar-chart", -->

<!--   color = "orange", -->

<!--   value = nrow(devices) -->

<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #| content: valuebox -->

<!-- #| title: "% fully functional" -->

<!-- list( -->

<!--   icon = "percent", -->

<!--   color = "green", -->

<!--   value = format(100*sum(devices$functionality == "fully functional")/nrow(devices), digits = 3) -->

<!-- ) -->

<!-- ``` -->

<!-- ## Row {orientation="columns"} -->

## Row {.tabset}

### Introduction Supply Mix {.tabset}

```{r}
#| title: "Facility Overview"

# 1. Count systems per facility and assign Facility A, B, C...
facility_ranked <- df|> 
  count(facility_name, name = "system_count") |> 
  arrange(desc(system_count)) |>    # highest first
  mutate(
    facility_clean = paste0("Facility ", LETTERS[row_number()])
  )

# 2. Join back and order factor levels so Facility A is on top in coord_flip()
df_plot <- df |> 
  left_join(facility_ranked, by = "facility_name") |> 
  mutate(
    facility_clean = factor(facility_clean, 
                            levels = rev(facility_ranked$facility_clean))
  ) 


type_levels <- c(
  "Generator",
  "Solar",
  "Solar, Battery",
  "Solar, Battery, Inverter",
  "Grid"
)

df_plot <- df_plot |>
  mutate(
    type = factor(type, levels = type_levels)
  )


# 3. Plot--------------------------------
ggplot(df_plot, aes(x = facility_clean, fill = type)) +
  geom_bar() +
  geom_boxplot(
    data = facility_ranked,
    aes(y = system_count),   # put boxplot on the count axis
    inherit.aes = FALSE,
    width = 0.8,
  ) +
  geom_text(
  aes(x = facility_clean, y = system_count, label = system_count),
  hjust = -0.3, size = 3) +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Energy System Category") +
  theme_minimal() +
  scale_fill_colorblind() 

#-----------------------------------------
df_plot_functional <- df_plot |> 
  filter(functional_now == "Yes")

ggplot(df_plot_functional, aes(x = facility_clean, fill = type)) +
  geom_bar() +
  geom_boxplot(
    data = facility_ranked,
    aes(y = system_count),   # put boxplot on the count axis
    inherit.aes = FALSE,
    width = 0.8,
  ) +
  geom_text(
  aes(x = facility_clean, y = system_count, label = system_count),
  hjust = -0.3, size = 3) +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Energy System Category") +
  theme_minimal() +
  scale_fill_colorblind() 

```

```{r}
#| title: "Literature Comparison"

literature_comparison <- combined |> 

  mutate(
    energy_quality = case_when(
    #outage_frequency %in% c("Every week", "Every two weeks", "Every ") ~ "Stable grid",
    is.na(main_elec) ~ "Non-grid: No electricity",
    main_elec %in% "Solar" ~ "Non-grid: Off-grid",
    type %in% "Solar, Battery, Inverter" ~ "Unstable Grid: Interrupted Grid with Back-up",
    TRUE ~ "Unstable Grid: Interrupted Grid without Back-up"
  )) |>
  group_by(facility_id) |>
  mutate(
    energy_quality = case_when(
      any(type %in% "Solar, Battery, Inverter", na.rm = TRUE) ~
        "Unstable Grid: Interrupted Grid with Back-up")
  )


literature_comparison <- combined |>
  group_by(facility_id) |>
  mutate(
    energy_quality = case_when(

      # Off-grid FIRST (must come before override)
      main_elec == "Solar" ~
        "Non-grid: Off-grid",

      is.na(main_elec) ~
        "Non-grid: No electricity",

      # Facility-level override ONLY for grid-connected systems
      any(type == "Solar, Battery, Inverter", na.rm = TRUE) &
        main_elec != "Solar" ~
        "Unstable Grid: Interrupted Grid with Back-up",

      TRUE ~
        "Unstable Grid: Interrupted Grid without Back-up"
    )
  ) |>
  ungroup()






categories <- c(
  "Non-grid: No electricity",
  "Non-grid: Off-grid",
  "Stable grid: Uninterrupted Grid with Back-up",
  "Unstable Grid: Interrupted Grid with Back-up",
  "Unstable Grid: Interrupted Grid without Back-up",
  "Unstable Grid: Uninterrupted Grid without Back-up"
)

categories <- c(
  "Unstable Grid: Uninterrupted Grid without Back-up",
  "Unstable Grid: Interrupted Grid without Back-up",
  "Unstable Grid: Interrupted Grid with Back-up",
  "Stable grid: Uninterrupted Grid with Back-up",
  "Non-grid: Off-grid",
  "Non-grid: No electricity"
)

third_pillar <- literature_comparison |>
  count(energy_quality, name = "value") |>
  mutate(
    value = value / sum(value) * 100,
    year = "2025",
    category = energy_quality
  ) |>
  select(year, category, value)




#--------------


suhlrie_hhfa <- tribble(
  ~year,        ~category, ~value,
  "2013/2014",  categories[1], 7.17,
  "2013/2014",  categories[2], 33.29,
  "2013/2014",  categories[3], 4.67,
  "2013/2014",  categories[4], 9.86,
  "2013/2014",  categories[5], 30.34,
  "2013/2014",  categories[6], 15,

  "2018/2019",  categories[1], 1.07,
  "2018/2019",  categories[2], 29.48,
  "2018/2019",  categories[3], 23.09,
  "2018/2019",  categories[4], 20.78,
  "2018/2019",  categories[5], 20.07,
  "2018/2019",  categories[6], 6,

  # third pillar with random values
  "2025",  categories[1], 1/20*100,
  "2025",  categories[2], 8/20*100,
  "2025",  categories[4], 7/20*100,
  "2025",  categories[5], 4/20*100)


colors <- c(
  "Unstable Grid: Uninterrupted Grid without Back-up" = "#5A82B9",
  "Unstable Grid: Interrupted Grid without Back-up"   = "#B24641",
  "Unstable Grid: Interrupted Grid with Back-up"      = "#9BB650",
  "Stable grid: Uninterrupted Grid with Back-up"      = "#7263AC",
  "Non-grid: Off-grid"                                 = "#63C3D1",
  "Non-grid: No electricity"                          = "#F29C38"
)


ggplot(suhlrie_hhfa, aes(x = year, y = value, fill = category)) +
  geom_col(width = 0.65) +
  geom_text(aes(label = round(value, 2)),
            position = position_stack(vjust = 0.5),
            color = "black", size = 3) +
  scale_fill_manual(values = colors) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  labs(x = NULL, y = NULL, fill = "Energy Supply Category") +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )

```

### Functionality {.tabset}

```{r}
#| title: "Functionality Overview"


# -----------------------------
# 1) Facility plot (counts)
# -----------------------------
facility_ranked <- df |>
  count(facility_name, name = "system_count") |>
  arrange(desc(system_count)) |>
  mutate(facility_clean = paste0("Facility ", LETTERS[row_number()]))

functionality_overview <- df |>
  left_join(facility_ranked, by = "facility_name") |>
  filter(!is.na(functional_now))

p_facility <-
  ggplot(functionality_overview,
         aes(x = fct_rev(fct_infreq(facility_clean)), fill = functional_now)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = NULL, y = "Energy System Count", fill = "Functionality", tag = "(c)") +
  theme_minimal() +
  scale_fill_colorblind()

# -----------------------------
# 2) Type plot (counts, horizontal)  + labels
# -----------------------------
functionality_supply_categories <- df |>
  filter(!is.na(functional_now))

p_type <-
  ggplot(functionality_supply_categories,
         aes(x = fct_rev(fct_infreq(type)), fill = functional_now)) +
  geom_bar() +
  geom_text(
    stat = "count",
    aes(label = after_stat(count)),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold",
    size = 3
  ) +
  coord_flip() +
  labs(x = NULL, y = "Energy System Count", fill = "Functionality", tag = "(d)") +
  theme_minimal() +
  scale_fill_colorblind() +
  theme(legend.position = "none")

# -----------------------------
# 3) Overall proportions (single bar)
# -----------------------------
overall_prop <- functionality_overview %>%
  count(functional_now) %>%
  mutate(prop = n / sum(n))

p_overall <-
  ggplot(overall_prop,
         aes(x = "All\nFacilities", y = prop, fill = functional_now)) +
  geom_col(width = 0.8) +
  coord_flip() +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(x = NULL, y = NULL, fill = "Functionality", tag = "(a)") +
  theme_minimal() +
  scale_fill_colorblind() +
  theme(legend.position = "none")

# -----------------------------
# 4) Time dependency (percent + count)
# -----------------------------
breaks <- seq(2000, 2027, by = 3)
year_labels <- c(
  "2000–2002","2003–2005","2006–2008","2009–2011","2012–2014",
  "2015–2017","2018–2020","2021–2023","2024–2025"
)

functionality_over_time <- df |>
  filter(!is.na(functional_now),
         installation_year != -99,
         type != "Grid") |>
  mutate(installation_year = as.numeric(installation_year)) |>
  filter(!is.na(installation_year)) |>
  mutate(
    year_bin = cut(
      installation_year,
      breaks = breaks,
      right = FALSE,
      include.lowest = TRUE,
      labels = year_labels
    )
  )

p_time_pct <-
  ggplot(functionality_over_time, aes(x = year_bin, fill = functional_now)) +
  geom_bar(position = "fill") +
  geom_text(
    stat = "count",
    aes(label = after_stat(count)),
    position = position_fill(vjust = 0.5),
    color = "white",
    fontface = "bold",
    size = 3
  ) +
  labs(x = "Installation Year", y = NULL, fill = "Functionality", tag = "(b)") +
  theme_minimal() +
  scale_fill_colorblind() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(drop = FALSE) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 30, hjust = 1)
  )
   





# -----------------------------
# 5) Arrange ALL plots nicely (single output)
# -----------------------------
  (p_overall | p_time_pct) /
  (p_facility | p_type) +
  plot_layout(heights = c(3, 6), guides = "collect") +
  plot_annotation(title = NULL) &
  theme(legend.position = "bottom")


```

```{r}
#| title: "Grid Reliability"

grid_reliability <- combined |> 
  distinct(facility_id, .keep_all = TRUE) |> 
  filter(!is.na(outage_frequency))


freq_levels <- c(
  "Never",
  "Rarely",
  "Every month",
  "Every two weeks",
  "Every week",
  "Every 3-4 days",
  "Every 2 days",
  "Every day",
  "Multiple times a day"
)


grid_reliability_plot <- grid_reliability |>
  mutate(
    outage_frequency = factor(
      outage_frequency,
      levels = freq_levels
    )
  )

freq_map <- c(
  "Never"               = 365,
  "Rarely"              = 60,
  "Every month"         = 30,
  "Every two weeks"     = 14,
  "Every week"          = 7,
  "Every 3-4 days"      = 4,
  "Every 2 days"        = 2,
  "Every day"           = 1,
  "Multiple times a day" = 0.5
)


grid_reliability_plot <- grid_reliability |>
  mutate(
    outage_frequency = factor(outage_frequency, levels = freq_levels),
    freq_days = freq_map[outage_frequency] |> as.numeric()
  )


ggplot(grid_reliability_plot,
       aes(x = freq_days,
           y = outage_duration,
           color = region,
           shape = region)) +
  geom_jitter(width = 0.1, height = 0.1, size = 10, alpha = 0.7) +
  scale_x_reverse(
    breaks = unname(freq_map),        # <- numeric only
    labels = names(freq_map)          # <- labels
  ) +
  geom_boxplot(
    data = grid_reliability_plot,
    aes(x = max(freq_days, na.rm = TRUE) + 2, y = outage_duration),  # <- left side after reverse
    inherit.aes = FALSE,
    width = 0.8
  ) +
  scale_y_continuous(breaks = seq(0, 15, 2), limits = c(0, NA)) +
  labs(
    x = "How often is there a grid outage?",
    y = "Grid Outage Duration [h]",
    color = "Region",
    shape = "Region"
  ) +
  theme_minimal() +
  scale_color_colorblind() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))


```

```{r}
#| title: "Nights without Light"

systemcountvsnightsnolight <- combined |> 
  filter(type != "Solar") |> 
  add_count(facility_id, name = "system_count") |> 
  distinct(facility_id, .keep_all = TRUE) |> 
  filter(night_treatments_monthly != -99) |> 
  mutate(dark_treatment_ratio = night_treatments_in_darkness_monthly / night_treatments_monthly * 100)

ggplot(data = systemcountvsnightsnolight,
       mapping = aes(x = system_count, 
                     y = night_treatments_in_darkness_monthly, 
                     color = night_treatments_monthly,
                     shape = main_elec)) +
  geom_jitter(width = 0.2, height = 0.3, size = 10, alpha = 0.7) +   # jittered points
  geom_boxplot(
    aes(x = system_count, y = -5),   # put boxplot on the count axis
    inherit.aes = FALSE,
    width = 3
  ) +
  geom_boxplot(
    aes(x = 0, y = night_treatments_in_darkness_monthly),   # put boxplot on the count axis
    inherit.aes = FALSE,
    width = 0.8
  ) +
    scale_x_continuous(breaks = seq(0, 10, 2)) +
  labs(x = "Energy System Count (without direct solar)",
       y = "Monthly night treatments without light",
       color = "Monthly night treatments",
       shape = "Primary electricity source") +
  theme_minimal()

#------------------------------

ggplot(data = systemcountvsnightsnolight,
       mapping = aes(x = system_count, 
                     y = dark_treatment_ratio, 
                     color = night_treatments_monthly
                     )) +
  geom_jitter(width = 0.3, height = 2, size = 5, alpha = 0.9) + 
  geom_hline(
  yintercept = 0,
  linetype = "dashed",
  color = "grey50"
  ) +
  geom_vline(
  xintercept = 0,
  linetype = "dashed",
  color = "grey50"
  ) +
  geom_boxplot(aes(x = system_count, y = -20),
                   width = 10,
                 inherit.aes = FALSE) +
  geom_boxplot(aes(x = -1, y = dark_treatment_ratio),
                   width = 1,
                 inherit.aes = FALSE,) +
  scale_x_continuous(breaks = seq(0, 12, 2)) +
  scale_y_continuous(breaks = seq(0,100,20),
                     labels = scales::label_percent(scale = 1)) +
  scale_color_gradient2(
  low = "#2166AC",
  mid = "#CFCFC4",
  high = "#B2182B",
    midpoint = median(systemcountvsnightsnolight$night_treatments_monthly, na.rm = TRUE)
                        ) +
  labs(x = "Energy System Count (without direct solar)",
       y = "Night Treatments without Lighting",
       color = "Monthly Night\nTreatments [count]",
       shape = "Primary Source") +
  theme_minimal()




```

# Install and Forget

## Row {.tabset}

### Installers vs Maintainers {.tabset}

```{r}
#| title: "Installers/Funders"

installers <- df |>
  mutate(
    funding = case_when(
      funding %in% c("MoH", "Staff", "EGPAF") ~ "DHO/MoH/Gov",
      is.na(funding) ~ "Unknown",
      TRUE ~ "Donor"
    ),
    # Explicit factor ordering for legend and stack order
    funding = factor(funding, levels = c("DHO/MoH/Gov", "Unknown", "Donor"))
  )

installers_plot <- ggplot(installers, aes(x = fct_rev(fct_infreq(type)), fill = funding)) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  # scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Initial Funder") +
  theme_minimal() +
  scale_fill_viridis_d(option = "D")

installers_plot
```

```{r}
#| title: "Repair Primary"

repair_primary_plot <- ggplot(df, aes(x = fct_rev(fct_infreq(type)), fill = repair_duty)) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  # scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Repair Duty") +
  theme_minimal() +
  scale_fill_viridis_d(option = "D")

repair_primary_plot


```

```{r}
#| title: "Funder vs Maintainers"

installers_plot <- installers_plot +
  labs(
    title = "Initial Funder",
    fill = NULL,
    tag = "(a)",
    y = "                                                      Energy System Count" 
  )

repair_primary_plot <- repair_primary_plot +
  labs(title = "Repair Primary", fill = NULL, tag = "(b)") + 
  theme(
    legend.position = "none",
    axis.text.y  = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  )

(installers_plot | repair_primary_plot) +
  plot_layout(heights = c(3, 6), guides = "collect") +
  plot_annotation(title = NULL) &
  theme(legend.position = "bottom")


```

### Maintenance {.tabset}

```{r}
#| title: "Repair & Maintenance & Trained Staff on Site"



staff_levels <- c("No", "Partially", "Yes")
pm_levels <- c("Never",
               "Sometimes but not routinely",
               "Routinely")

maintenance_count <- kobo_questionnaire |> 
  mutate(
    trained_staff_energy_system =
      factor(trained_staff_energy_system, levels = staff_levels),
    preventive_maintenance_carried_out =
      factor(preventive_maintenance_carried_out, levels = pm_levels))


staff_count <- maintenance_count |>
  mutate(trained_staff_energy_system = replace_na(trained_staff_energy_system, "No")) |>
  count(trained_staff_energy_system, name = "n")

pm_count <- maintenance_count |>
  mutate(preventive_maintenance_carried_out = replace_na(preventive_maintenance_carried_out, "Never")) |>
  count(preventive_maintenance_carried_out, name = "n")

combined_counts <- bind_rows(
  staff_count |>
    rename(Response = trained_staff_energy_system) |>
    mutate(Question = "Is there a trained staff member on site?"),
  pm_count |>
    rename(Response = preventive_maintenance_carried_out) |>
    mutate(Question = "Is preventive maintenance carried out on any energy system?")
)



combined_counts |>
  gt(groupname_col = "Question") |>
  tab_header(
    title = "Maintenance & Repair",
    subtitle = "Data from 20 health centres"
  ) |>
  cols_label(
    Response = "",
    n = ""
  ) |>
  opt_stylize(style = 1)

```

```{r}
#| title: "Repair Success Rate"

repair_success_rate <- combined |> 
  filter(!is.na(repair_success))

ggplot(repair_success_rate, aes(x = fct_rev(fct_infreq(type)), fill = repair_success)) +
  geom_bar() +
  coord_flip() +
  # scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = NULL,
       y = "Reported System Failures",
       fill = "Repaired") +
  theme_minimal() +
  scale_fill_manual(values = c("Yes" = "lightblue", "No" = "black"))
```

# Donor Alignment

## Row {.tabset}

### Donor Variation {.tabset}

```{r}
#| title: "Donor Variation Overview"

# 1) Count systems per facility and assign Facility A, B, C...
facility_ranked <- df |>
  count(facility_name, name = "system_count") |>
  arrange(desc(system_count)) |>
  mutate(facility_clean = paste0("Facility ", LETTERS[row_number()]))

# 2) Join back and order factor levels so Facility A is on top in coord_flip()
df_plot <- df |>
  left_join(facility_ranked, by = "facility_name") |>
  mutate(
    facility_clean = factor(
      facility_clean,
      levels = rev(facility_ranked$facility_clean)
    )
  )

# 3) Clean funding: handle real NA + "NA" string + blanks; mark as missing placeholder
df_clean <- df_plot |>
  mutate(
    funding_chr = as.character(funding),
    funding_chr = na_if(funding_chr, "NA"),
    funding_chr = na_if(funding_chr, ""),
    funding_chr = if_else(is.na(funding_chr), "__missing__", funding_chr)
  )

# 4) Donor mapping ONLY for real donors (exclude MoH and missing)
donor_map <- df_clean |>
  filter(funding_chr != "MoH", funding_chr != "__missing__") |>
  count(funding_chr, sort = TRUE) |>
  mutate(funding_label = paste0("Donor ", LETTERS[row_number()])) |>
  select(funding_chr, funding_label)

# 5) Recode: MoH -> DHO/MoH/Gov; missing -> Unknown; others -> Donor A/B/...
df_plot2 <- df_clean |>
  left_join(donor_map, by = "funding_chr") |>
  mutate(
    funding_recode = case_when(
      funding_chr == "MoH"         ~ "DHO/MoH/Gov",
      funding_chr == "__missing__" ~ "Unknown",
      TRUE                         ~ funding_label
    )
  )

# 6) Plot
ggplot(df_plot2,
       aes(x = fct_rev(fct_infreq(facility_clean)),
           fill = fct_infreq(funding_recode))) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(
    x = NULL,
    y = "Energy System Count",
    fill = "Initial Funder"
  ) +
  theme_minimal() +
  scale_fill_viridis_d(option = "H")


```

```{r}
#| title: "Supply Category Donors"

# ggplot(df_plot, aes(x = fct_rev(fct_infreq(type)), fill = fct_infreq(funding))) +
#   geom_bar(position = position_stack(reverse = TRUE)) +
#   coord_flip() +
#   # scale_y_continuous(breaks = seq(0, 10, 2)) +
#   labs(x = "Category",
#        y = "Count",
#        fill = "Funder") +
#   theme_minimal() +
#   scale_fill_viridis_d(option = "H")
#   # scale_fill_colorblind()

ggplot(df_plot2,
       aes(x = fct_rev(fct_infreq(type)),
           fill = fct_infreq(funding_recode))) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  labs(x = "Category",
       y = "Count",
       fill = "Funder") +
  theme_minimal() +
  scale_fill_viridis_d(option = "H")

```

### Manufacturer Variation {.tabset}

```{r}
#| title: "Supply Categories Manufacturers"

ggplot(combined, aes(x = fct_rev(fct_infreq(type)), fill = brand)) +
  geom_bar() +
  coord_flip() +
  # scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = "Category",
       y = "Count",
       fill = "Manufacturer") +
  theme_minimal() 
  # scale_fill_colorblind()


```

```{r}
#| title: "District Supply Categories Manufacturers"

district_manufacturers <- combined |>
  mutate(district_label = paste("District", LETTERS[as.numeric(factor(district))])) |> 
  filter(type != "Generator", 
         type != "Grid",
         ) |> 
  mutate(brand = replace_na(brand, "Unknown"))

ggplot(district_manufacturers, aes(x = fct_rev(fct_infreq(type)), fill = brand)) +
  geom_bar() +
  coord_flip() +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Manufacturer") +
  theme_minimal() +
  facet_wrap(~ district_label)


```

```{r}
#| title: "Manufacturers in each Facility"

ggplot(df, aes(x = fct_rev(fct_infreq(facility_name)), fill = brand)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = "Facility Name",
       y = "Count",
       fill = "Manufacturer") +
  theme_minimal()
```

### Variation Index {.tabset}

```{r}
#| title: "Variation "

facility_ranked <- df |>
  count(facility_name, name = "system_count") |>
  arrange(desc(system_count)) |>
  mutate(facility_clean = paste0("Facility ", LETTERS[row_number()]))

funder_diversity <- df |>
  mutate(
    funding_clean = case_when(
      funding %in% c("MoH", "Staff", "EGPAF") ~ "DHO/MoH/Gov",
      is.na(funding) | funding == ""           ~ "Unknown",
      TRUE                                     ~ funding
    )
  ) |>
  filter(funding_clean != "Unknown") |>          # exclude unknown from index
  group_by(facility_id, funding_clean) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(facility_id) |>
  mutate(p_i = n / sum(n)) |>
  summarise(
    n_systems         = sum(n),
    n_funders         = n_distinct(funding_clean),
    simpson_diversity = 1 - sum(p_i^2),
    .groups = "drop"
  )

funder_diversity <- df |>
  mutate(
    funding_clean = case_when(
      funding %in% c("MoH", "Staff", "EGPAF") ~ "DHO/MoH/Gov",
      is.na(funding) | funding == ""           ~ "Unknown",
      TRUE                                     ~ funding
    )
  ) |>
  filter(funding_clean != "Unknown") |>          # exclude unknown from index
  group_by(facility_id, funding_clean) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(facility_id) |>
  mutate(p_i = n / sum(n)) |>
  summarise(
    n_systems         = sum(n),
    n_funders         = n_distinct(funding_clean),
    simpson_diversity = 1 - sum(p_i^2),
    .groups = "drop"
  )

mfr_diversity <- df |>
  mutate(
    component_brand = case_when(
      !is.na(inverter_manufacturer) ~ inverter_manufacturer,
      !is.na(brand)                 ~ brand,
      TRUE                          ~ NA_character_
    )
  ) |>
  filter(!is.na(component_brand), component_brand != "Unknown") |>
  group_by(facility_id, component_brand) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(facility_id) |>
  mutate(p_i = n / sum(n)) |>
  summarise(
    n_brands    = n_distinct(component_brand),
    simpson_mfr = 1 - sum(p_i^2),
    .groups = "drop"
  )

func_ratio <- df |>
  filter(!is.na(functional_now)) |>
  mutate(
    is_nonfunctional = case_when(
      functional_now == "No"        ~ 1,
      functional_now == "Partially" ~ 0.5,
      functional_now == "Yes"       ~ 0
    )
  ) |>
  group_by(facility_id) |>
  summarise(
    n_systems_total = n(),
    prop_nonfunc    = mean(is_nonfunctional),
    .groups = "drop"
  )

df_analysis <- funder_diversity |>
  left_join(mfr_diversity,    by = "facility_id") |>
  left_join(func_ratio,       by = "facility_id") |>
  left_join(facility_ranked |> select(facility_name, facility_clean),
            by = character())  # needs facility_id bridge via df first

# Safer: bring facility_name from df, then join
facility_meta <- df |>
  distinct(facility_id, facility_name) |>
  left_join(facility_ranked, by = "facility_name") |>
  left_join(
    kobo_questionnaire |> select(facility_id, region, district),
    by = "facility_id"
  )

df_analysis <- funder_diversity |>
  left_join(mfr_diversity,  by = "facility_id") |>
  left_join(func_ratio,     by = "facility_id") |>
  left_join(facility_meta,  by = "facility_id")

# Funder diversity (Simpson) vs. non-functionality
  # Funder diversity (Simpson) vs. non-functionality
cor.test(df_analysis$simpson_diversity, df_analysis$prop_nonfunc,
         method = "spearman")

# Raw funder count vs. non-functionality (simpler, more interpretable)
cor.test(df_analysis$n_funders, df_analysis$prop_nonfunc,
         method = "spearman")

# Manufacturer brand diversity vs. non-functionality
cor.test(df_analysis$simpson_mfr, df_analysis$prop_nonfunc,
         method = "spearman")
```

```{r}
plot_scatter <- function(data, x_var, x_lab) {
  ggplot(data, aes(x = .data[[x_var]], y = prop_nonfunc,
                   colour = region, label = facility_clean)) +
    geom_point(size = 4, alpha = 0.8) +
    geom_smooth(method = "lm", se = TRUE,
                colour = "grey40", linetype = "dashed", linewidth = 0.7) +
    geom_text_repel(size = 2.8, max.overlaps = 15) +
    scale_y_continuous(labels = percent_format(accuracy = 1),
                       limits = c(0, 1)) +
    scale_color_colorblind() +
    labs(x = x_lab,
         y = "Proportion of non-functional systems",
         colour = "Region") +
    theme_minimal(base_size = 11)
}

p1 <- plot_scatter(df_analysis, "simpson_diversity",
                   "Funder diversity (Simpson index)")
p2 <- plot_scatter(df_analysis, "n_funders",
                   "Number of distinct funders")
p3 <- plot_scatter(df_analysis, "simpson_mfr",
                   "Manufacturer diversity (Simpson index)")

p1 / p2 / p3 +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
```

```{r}
donor_map <- df |>
  mutate(
    funding_chr = as.character(funding),
    funding_chr = na_if(funding_chr, "NA"),
    funding_chr = na_if(funding_chr, ""),
    funding_chr = if_else(is.na(funding_chr), "__missing__", funding_chr)
  ) |>
  filter(funding_chr != "MoH", funding_chr != "__missing__") |>
  count(funding_chr, sort = TRUE) |>
  mutate(funding_label = paste0("Donor ", LETTERS[row_number()])) |>
  select(funding_chr, funding_label)

df_bar <- df |>
  mutate(
    funding_chr = as.character(funding),
    funding_chr = na_if(funding_chr, "NA"),
    funding_chr = na_if(funding_chr, ""),
    funding_chr = if_else(is.na(funding_chr), "__missing__", funding_chr)
  ) |>
  left_join(donor_map, by = "funding_chr") |>
  mutate(
    funding_recode = case_when(
      funding_chr == "MoH"         ~ "DHO/MoH/Gov",
      funding_chr == "__missing__" ~ "Unknown",
      TRUE                         ~ funding_label
    )
  ) |>
  left_join(
    df_analysis |> select(facility_id, facility_clean, simpson_diversity),
    by = "facility_id"
  ) |>
  mutate(
    facility_clean = fct_reorder(facility_clean, simpson_diversity)
  )

ggplot(df_bar,
       aes(x = facility_clean, fill = fct_infreq(funding_recode))) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Initial Funder",
       subtitle = "Ordered by funder diversity (most fragmented at top)") +
  theme_minimal() +
  scale_fill_viridis_d(option = "H")
```

```{r}
#| title: "Variation Scatter"

plot_scatter <- function(data, x_var, x_lab) {
  ggplot(data, aes(x = .data[[x_var]], y = prop_nonfunc,
                   colour = region, label = facility_clean)) +
    geom_point(size = 4, alpha = 0.8) +
    geom_smooth(method = "lm", se = TRUE,
                colour = "grey40", linetype = "dashed", linewidth = 0.7) +
    geom_text_repel(size = 2.8, max.overlaps = 15) +
    scale_y_continuous(labels = percent_format(accuracy = 1),
                       limits = c(0, 1)) +
    scale_color_colorblind() +
    labs(x = x_lab,
         y = "Proportion of non-functional systems",
         colour = "Region") +
    theme_minimal(base_size = 11)
}

p1 <- plot_scatter(df_analysis, "simpson_diversity",
                   "Funder diversity (Simpson index)")
p2 <- plot_scatter(df_analysis, "n_funders",
                   "Number of distinct funders")
p3 <- plot_scatter(df_analysis, "simpson_mfr",
                   "Manufacturer diversity (Simpson index)")

(p1 / p2 / p3) +
plot_layout(guides = "collect") &
theme(legend.position = "bottom")
```

```{r}
#| title: "Funder Composition Bar Chart"

donor_map <- df |>
  mutate(
    funding_chr = as.character(funding),
    funding_chr = na_if(funding_chr, "NA"),
    funding_chr = na_if(funding_chr, ""),
    funding_chr = if_else(is.na(funding_chr), "__missing__", funding_chr)
  ) |>
  filter(funding_chr != "MoH", funding_chr != "__missing__") |>
  count(funding_chr, sort = TRUE) |>
  mutate(funding_label = paste0("Donor ", LETTERS[row_number()])) |>
  select(funding_chr, funding_label)

df_bar <- df |>
  mutate(
    funding_chr = as.character(funding),
    funding_chr = na_if(funding_chr, "NA"),
    funding_chr = na_if(funding_chr, ""),
    funding_chr = if_else(is.na(funding_chr), "__missing__", funding_chr)
  ) |>
  left_join(donor_map, by = "funding_chr") |>
  mutate(
    funding_recode = case_when(
      funding_chr == "MoH"         ~ "DHO/MoH/Gov",
      funding_chr == "__missing__" ~ "Unknown",
      TRUE                         ~ funding_label
    )
  ) |>
  left_join(
    df_analysis |> select(facility_id, facility_clean, simpson_diversity),
    by = "facility_id"
  ) |>
  mutate(
    facility_clean = fct_reorder(facility_clean, simpson_diversity)
  )

ggplot(df_bar,
       aes(x = facility_clean, fill = fct_infreq(funding_recode))) +
  geom_bar(position = position_stack(reverse = TRUE)) +
  coord_flip() +
  labs(x = NULL,
       y = "Energy System Count",
       fill = "Initial Funder",
       subtitle = "Ordered by funder diversity (most fragmented at top)") +
  theme_minimal() +
  scale_fill_viridis_d(option = "H")
```


# Geographic

## Row {.tabset}

### Geocomputation with R {.tabset}

```{r}
#| title: "Malawian Health Centers"

# Get Malawi polygons at relatively high resolution
malawi <- rnaturalearth::ne_countries(
  country = "Malawi",
  scale = "large",        # "small", "medium", "large" (large = more detail)
  returnclass = "sf"
)


fac_sf <- kobo_questionnaire |> 
  st_as_sf(
    coords = c("gps_location_longitude", "gps_location_latitude"),
    crs = 4326,
    remove = FALSE
  )


tm_shape(malawi) +
  tm_polygons(fill = "grey95", col = "grey70") +
  tm_shape(fac_sf) +
  tm_symbols(
    size = "catchment_population_size",
    fill = "main_elec",
    col  = "black",
    size.scale = tm_scale_continuous(
      values.range = c(0.1, 1.5)   # min & max symbol size (adjust as needed)
    ),
    size.legend = tm_legend(title = "Catchment Population"),
    fill.legend = tm_legend(title = "Primary Electrification"),
    fill.scale = tm_scale_categorical(
  values = c("Grid" = "steelblue", "Mini-grid" = "red", "Solar" = "gold")
)

  ) +
  tm_layout(legend.outside = TRUE) 


#similar with ggplot----------------------------------------------------------

bbox <- st_bbox(malawi)

ggplot() +
  geom_sf(data = malawi, fill = "grey95", color = "grey70") +
  geom_sf(
    data = fac_sf,
    aes(size = catchment_population_size, color = main_elec),
    alpha = 0.8
  ) +
  scale_size_continuous(
    name  = "Catchment population",
    range = c(1, 7)
  ) +
  scale_color_brewer(
    name = "Primary electrification",
    palette = "Dark2"
  ) +
  coord_sf(
    xlim = c(bbox["xmin"], bbox["xmax"]),
    ylim = c(bbox["ymin"], bbox["ymax"])
  ) +
  labs(title = "Health facilities in Malawi") +
  theme_minimal()
```


# Climate Change

## Row {.tabset}

```{r}
#| title: "Climate Impacts"

impact_cols <- c(
  "parts_operations_affected_increase_seasonal_illnesses",
  "parts_operations_affected_increase",
  "parts_operations_affected_cough",
  "parts_operations_affected_decrease",
  "parts_operations_affected_decrease_wild_fires",
  "parts_operations_affected_decrease_lightning",
  "parts_operations_affected_injury_lightning",
  "parts_operations_affected_damage_buildings_equipment",
  "parts_operations_affected_electricity_reliability",
  "parts_operations_affected_water_availability",
  "parts_operations_affected_migration",
  "parts_operations_affected_not_seeking_care_outages",
  "parts_operations_affected_delayed_care_transportation",
  "parts_operations_affected_reduced_referral_ability",
  "parts_operations_affected_rooms_too_hot",
  "parts_operations_affected_dont_know"
)

impact_labels <- c(
  parts_operations_affected_increase_seasonal_illnesses =
    "Temporary increases in patients due to more malaria in the rainy season",

  parts_operations_affected_increase =
    "Temporary increases in patients due to malnutrition in long dry seasons",

  parts_operations_affected_cough =
    "Temporary increases in patients in cold, dry seasons due to dust in the air, causing cough",

  parts_operations_affected_decrease =
    "Temporary decreases in facility accessibility due to floods",

  parts_operations_affected_decrease_wild_fires =
    "Temporary decreases in facility accessibility due to wild fires",

  parts_operations_affected_decrease_lightning =
    "Temporary decreases in facility accessibility due to storms/cyclones",

  parts_operations_affected_injury_lightning =
    "Injuries because of storms/cyclones/lightnings",

  parts_operations_affected_damage_buildings_equipment =
    "Damage to infrastructure or energy systems or equipment because of storms/cyclones/lightnings",

  parts_operations_affected_electricity_reliability =
    "Grid is less reliable during dry seasons",

  parts_operations_affected_water_availability =
    "Decreased water availability",

  parts_operations_affected_migration =
    "Migration to/from the region due to weather/environment",

  parts_operations_affected_not_seeking_care_outages =
    "People not seeking care due to power outages",

  parts_operations_affected_delayed_care_transportation =
    "Delayed care-seeking due to transportation issues",

  parts_operations_affected_reduced_referral_ability =
    "Reduced ability to refer patients to other facilities due to weather",

  parts_operations_affected_rooms_too_hot =
    "Rooms too hot so doors have to be opened, affects privacy",

  parts_operations_affected_dont_know =
    "Don't know"
)



climate_impacts <- kobo_questionnaire |>
  summarise(
    across(
      all_of(names(impact_labels)),
      ~ sum(.x %in% c("Yes", TRUE, 1), na.rm = TRUE)
    )
  ) |>
  pivot_longer(
    everything(),
    names_to = "Impact",
    values_to = "Count"
  ) |>
  mutate(
    Impact = impact_labels[Impact] |> unname()
  )


climate_impacts |>
  arrange(desc(Count)) |>
  gt() |>
  tab_header(
    title = "Climate-related impacts on health facility operations"
  ) |>
  cols_label(
    Impact = "Impact",
    Count = "Number of facilities"
  ) |>
  opt_stylize(style = 1)


```

# Data

## Row {.tabset}

```{r}
#| title: "Energy Systems"

library(DT)

all_vars <- df |> 
  select(facility_id,
facility_name,
brand,
model,
description,
type,
use,
panel_count,
panel_size,
np_total_storage_capacity_wh,
storage_type,
battery_corrosion,
battery_dust,
inverter_manufacturer,
np_inverter_output_va,
charge_controller,
funding,
installer,
functional_donation,
installation_year,
functional_now,
failure_year,
disfunction_part,
disfunction_cause,
repair_duty,
repair_wait_time,
repair_success,
maintenance_by,
spare_parts,
remote_monitoring,
functional_but_unused_reason,
notes,
images
)
datatable(all_vars)


```

```{r}
#| title: "Kobo Questionnnaire"

datatable(kobo_questionnaire)
```

```{r}
#| title: "Combined"

datatable(combined)
```
